\documentclass[12pt, letterpaper]{memoir}
\title{The Sessions, The Play}
\author{Mustafif Khan}
\date{}
\usepackage{color}
\usepackage{hyperref}
\hypersetup{
colorlinks=true, % make the links colored
linkcolor=black, % color TOC links in blue
urlcolor=red, % color URLs in red
linktoc=all % 'all' will create links for everything in the TOC
}
\usepackage{dramatist}
\usepackage{calc}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{\thetitle}
\rhead{\theauthor}
\rfoot{Page \thepage}
\begin{document}
\maketitle
\pagenumbering{arabic}
%\newpage
%\paragraph{Characters}
\newpage
\tableofcontents
%Characters
\Character[Mustafif - a person]{M}{M}
\Character[Alternate Ego]{Alter Ego}{OM}
\Character[Therapist - a person]{Therapist}{T}
\Character[Singers - background singers]{Singers}{Sing}

%Lighting Cues
\Character[LX Solo- FOH1, LX3 @ Stage Right]{Lx-Solo}{Solo}
\Character[Lx Therapy Room- FOH1, LX1, LX3 @ Stage R, C, L]{Lx-TR}{TR}
\Character[Lx Madness- FOH1, LX1 @ Stage R, C, L]{Lx-Madness}{Mad}
\Character[Lx Multiple]{Lx-Multiple}{LM}



\setlength{\speakswidth}{\widthof{\speaksfont Therapist}}
\addtolength{\speakswidth}{\Dlabelsep}
\addtolength{\speaksindent}{\speakswidth}

\act[]
\scene[\textit{Technical Cues}]
\StageDir{
    \begin{center}
        Main Lighting Cues
    \end{center}
}
\begin{drama}
\Solospeaks{This lighting cue is used at any point for M's monologues or any point 
where he may be speaking to himself.\\\textbf{Position: FOH1, LX3 @ Stage R \& C}}
\TRspeaks{This lighting cue is used to situate the therapy room, this is used in scenes 
where M and the Therapist are together.\\\textbf{Position: FOH1, LX1, LX3 @ Stage R, C \& L}}
\Madspeaks{This lighting cue is used for rambling, when M is going back and forth, 
it is used to situate this madness.\\\textbf{Position: FOH1, LX1 @ Stage R, C, \& L}}
\LMspeaks{This will be used to describe multiple lighting transitions. Ex. 
Solo @ 50\% U3, Madness @ 10\% D2}
\end{drama}
\StageDir{
        If you have not a lighting technician or designer and want to understand these transitions, 
        a standard lighting cue may look like this: \\
        LX Cue @ Power Percentage Uptime/Downtime\\
        To describe the uptime and downtime you may see Ux or Dx where x is the transition time in seconds
}
\newpage
\scene[\textit{Prelude}]
\StageDir{
    \begin{center} 
        Starts with M in his room, sitting at his desk, writing on a notebook.
     \end{center}
}
\begin{drama}
    \Solospeaks{@ 50\% U3}
    \Mspeaks{I want to, I just want to\dots tell you something! I just want to\dots please just hear me out! I want to tell you I'm \textit{\%Attempts to say okay\%} FUCK!}
\end{drama}

\StageDir{
    \begin{center}
        Breaks pencil, slamming it on the table. Singers come up wearing all white in the background.
        M stands up and goes to Madness position once Solo blackouts. 
    \end{center}
}
\begin{drama}
    \LMspeaks{Solo @ 0\% D2.5, Lx 2 @ 30\% U3, Madness @ 70\% U2.5}
    \Mspeaks{How can I say words without doubting myself, huh!}
    \Singspeaks{\textit{He just wants to let you know, He just wants to say!}}
\end{drama}
\StageDir{
    \begin{center}
        M starts to argure with himself
    \end{center}
}
\begin{drama}
    \Mspeaks{How can I say words without thinking about the consequences that may be involved!}
    \OMspeaks{Not a thorough plan, no hide all the evidence, hide it!}
    \Mspeaks{Oh no, it's all part of the calculations, I have it don't I?}
    \OMspeaks{Don't kid yourself}
    \Mspeaks{You fucking said it was gone, you fucking said it was gone! I have depression,
     fuck! Clinical to the teenagers in our generation, boomers recall it to be non existent 
     in us. Why because we didn't fight in a war!}
    \Singspeaks{\textit{Misjudged, cautious of self's chance to hell, ohhh, he asks the lord if he's worthy to be in heaven}}
    \Mspeaks{I just wished I had someone I can tell all the time. Without being told not to 
    trust society, it's making me go crazy! I'm scared, I can't do it, I can't tell her, I can't fucking do it!}
    \Singspeaks{\textit{He asks why, he questions the reality he's living. Society is doing nothing, but to him they're looking down on him}}
    \OMspeaks{You can't, you can never! Never trust her, because that was 
    the first mistake you made! You fell in love, and that turned into madness, craziness into insanity, now look at the shit hole you digged yourself!}
    \Mspeaks{Shut the fuck up! Who did I show my slits to? Tell her my mind was swirling in turbulent thoughts! 
    I was afraid of seeing tomorrow's promise, who was one of the people who helped me recover!}
    \OMspeaks{If you recovered, then why are you here!}
\end{drama}
\StageDir{
    \begin{center}
        M goes down crying on his chair, the desk is moved and the Therapist comes sitting on a chair
    \end{center}
}
\begin{drama}
    \LMspeaks{Lx 2 @ 0\% D3, Madness @ 0\% D3, TR @ 80\% U3}
    \Tspeaks{Welcome, you will be here for 15 sessions to help you recover. 
    After your little incident, I hope I can help you}
\end{drama}
\StageDir{
    \begin{center}
        Scene ends and move to a Therapist room setting
    \end{center}
}
\begin{drama}
    \TRspeaks{@ 50\% D3}
\end{drama}
\newpage
\scene[\textit{The Session}]
\begin{drama}
    \Tspeaks{So please tell me what's wrong?}
    \Mspeaks{I....I....I...}
    \Tspeaks{You know you can tell me anything}
    \Tspeaks{So please tell me what happened}
\end{drama}
\StageDir{M stands up to speak}
\begin{drama}
    \LMspeaks{Solo @ 70\% U2}
    \Mspeaks{I opened a door to the underworld! They told me they'd help me, I regret it! 
    Demons of my past haunting me! Don't call it paranormal until it takes my soul. 
    Takes me whole as it swallows...trying to be tranquil...when it's getting me shooked, 
    hooked on these ideas slowly eating me}
    \OMspeaks{Welcome to the session}
\end{drama}
\StageDir{M sits back down}
\begin{drama}
    \LMspeaks{TR @ 70\% U3, Solo 0\% D3}
    \Tspeaks{So you feel like you still haven't recovered?}
    \Tspeaks{Depression and suicide still in your mind?}
    \Mspeaks{Recovering from suicide but depression still in question. 
    Isolated and feeling hated, insecurities are feeling like a melody, they sing me a song. 
    I say fuck it to my decision, I ain't talking to her about it!}
    \Tspeaks{You tend to lie a lot? Is it because you don't like being honest, or are you scared to be?}
    \LMspeaks{Solo @ 70\% U1.5, TR @ 40\% D1.5}
    \Mspeaks{Yeah I lie, fucking lie down, act like I'm dead so I can get buried alive! 
    \%Whispers\% A self defense mechanic, trying to tell but told don't. I'm holding back words, and they're holding me back,
    hard to share my vision when I'm the only one seeing it. I tell the truth, they're not happy with it! I share a lie, they don't notice, they find out and ask why I did it. 
    I tell them I didn't notice. \%Whispers\% When I force my mind to forget. \%Preach\% I swear because I'm insecure! I lie because I don't want to show my colours, so I said fuck it! Now I'm in a session!}
\end{drama}
\StageDir{Lighting goes back to normal hihlighting M and the Therapist}
\begin{drama}
    \Tspeaks{Interesting, very interesting. Well Mr.Khan this is all the time we have, see you in the next session.}
\end{drama}
\StageDir{Lights dim, and the Therapist leaves, leaving light focus on M}
\begin{drama}
    \Mspeaks{How do I always manage to come back, salute myself back into solitude, I got cold feet
    in this Tundra of emotions washing on me. Breakdowns leaving me in turbulent troubles, 
    I ask myself if this girl is even worth the trouble? 
    Worried and confused about someone else's well being, I forgot to notice mine.
    Tears showing my fears, I jot them in poems. I learned to draw art
    in a form of my words, rhyming turning into shades, I sketch ideas for my next drawings, 
    the portrait of my pain. The anthology of my dark thoughts...}
\end{drama}
\StageDir{M sits down, and light comes back to therapist room}

\scene[Social Workers]
\StageDir{
    \begin{center}
    Therapist comes back in
    \end{center}
}
\begin{drama}
    \Tspeaks{Hello, welcome back! So I wanted to talk about one of your poems?}
    \Mspeaks{I have over 60 poems, you gotta be more specific?}
    \Tspeaks{It's in your anthology, Mental Health}
    \Mspeaks{Well what's wrong?}
    \Tspeaks{What do you mean by your own knife?}
    \Mspeaks{I attempted once...I was scared, I just needed to tell someone}
\end{drama}
\StageDir{
    \begin{center}
        Social workers come in
    \end{center}
}
\begin{drama}
    \Tspeaks{Tell it to the social workers and I}
\end{drama}
\StageDir{\begin{center}
    Lights go down to 55\% at the Therapist and social workers
\end{center}}
\begin{drama}
    \Mspeaks{Confidentiality ending with suicidal behaviour, so why expect me to talk about suicide? \%Acts Worried\% You see, I have expectations and math makes me so stressed. I lied, I avoided the chance to get professional help with the depression I kept under the rug.
    It's my problem, how could they help me! Math ended up stressing me a lot, integrals differentiating my mind, the thing is 
    I ended up not lying...they told me to take deep breaths and relax. Something I tend currently tend to do...listen to Dre while my eyes are closed. 
    The fact that I'm happy without a slashed wrist bleeding, I call that a recovery, so you know what? 
    \par Yeah I fucking wrote it, I was scared, and felt alone. I wrote it in rhymes to tell my teacher I was scared I would
    kill myself! Becoming gluten free, I chose to be anorexhic! Losing 10 pounds in a month, why not be skinnier than a twig?
    I was confused as hell! Accepting hell was where I belong, I said fuck you to god. But I'm not scared
    anymore to say I suffered from mental illness...to say it's your choice whether it stays or leaves you!}
\end{drama}
\StageDir{\begin{center}
    Lights at Therapist restore to F
\end{center}}
\begin{drama}
    \Tspeaks{Well we will need to check on you every so often}
    \Mspeaks{Fair enough, are we done here?}
    \Tspeaks{Yes, good job today!}
\end{drama}
\StageDir{
    \begin{center}
      Both leave the room, lights dim  
    \end{center}
    }
\scene[\textit{Political Stupidity}]
\StageDir{\begin{center}
    Therapist sits on his chair, M is standing up glancing in a far distance, opposite to the Therapist
\end{center}}
\begin{drama}
    \Tspeaks{So when did you start getting into politics?}
    \Mspeaks{When I was in 10}
    \Tspeaks{How about reading newspapers?}
    \Mspeaks{11}
    \Tspeaks{How do you feel politics is right now?}
    \Mspeaks{It's being fucking retarded!}
\end{drama}
\StageDir{M faces the Therapist as if he is giving a lecture}
\begin{drama}
    \Mspeaks{America is being ran by an orange! Fucking closed by the world, break the door hinge,
    they're acting extra terrestrial! Get George Lucas, yet another starwars episode coming along. 
    \par Let's see...evil dictator, crumbling economy, wars??? This is what I call political stupidity!}

    \Tspeaks{So how about abortion? What are your opinions about it?}
    \Mspeaks{Well a person ain't a person until its born, murder is taking the life of a person.
    If a women can't take care of it, why have a baby go through so much trouble. A tumbling life, 
    why gamble on it? If a women got raped, then should this sperm be taped onto her life? White 
    people please confirm this? Because yet you complain about it, you don't seem to consider innocent 
    bystander's death, MURDER!} 
    \Tspeaks{Well, I guess my next question is your views on white people?}
    \Mspeaks{Well...you can't judge a race by some's actions. Some live by the idea of superiorty, 
    when white's population makes them feel minor! Calling negros criminals, fucking fat man, trying to fuck up this world, they call it Nagasaki.
    Fucking colonists! Nazis without a swastika, KGB without the secret, problem is...it's not only white people, it's every person who think they're superior...
    Nationalistic Ideals....That's what I call political stupidity.}
\end{drama}
\StageDir{\begin{center}
    Lights focussed on M
\end{center}}
\begin{drama}
    \Mspeaks{I always wondered what beauty really means...a word redefined throughout history. Is it to measure 
    someone's body, how big the boner be....or is it really the personality of the person. Internal and external 
    are both qualities in our mind, the difference between a pervert and a gentlemen is he knows what's more desired.}
\end{drama}
\newpage
\scene[Intoxicated]
\StageDir{\begin{center}
    Lights go back to normal
\end{center}}
\begin{drama}
    \Tspeaks{Please tell me, how do you fell when you meet a nice girl you may like?}
    \Mspeaks{Well I kinda feel like...}
\end{drama}
\StageDir{\begin{center}
    M stands up
\end{center}}
\begin{drama}
    \Mspeaks{I'm intoxicated, excited to meet this person, did I take heroine? I've never been so exicted to meet someone...it's 
    very nice to meet you, how could I be fated to see you? Are you my soul mate? For goodness sake forget it, you're probably fake...}
\end{drama}
\StageDir{\begin{center}
    M sits back down
\end{center}}
\begin{drama}
    \Tspeaks{I see...you give up quite easily don't you?}\
    \Mspeaks{What makes you say that?}
    \Tspeaks{Hmmm...well tell me more?}
\end{drama}
\StageDir{\begin{center}
    M stands back up
\end{center}}
\begin{drama}
    \Mspeaks{She's leaving me speechless, I feel like I'm going to faint because I may be falling in love with her. 
    Gravity is bringing me down, her beauty is dragging me down, beauty turning into blushes, I got a new crush! Next thing you
    know she's just a memory I lost interest in, it can be a week or a year...But this girl is really nice, I got a good feeling about her.}
    \Tspeaks{So then, do you try to get a date with her or...}
    \Mspeaks{I don't do shit! Get depressed in a fantasy I settle my self in, not being able to fit in a relationship, I complain I'm lonely!
    I complain...but the thing is, I didn't do anything...I'm hopeless}
    \Tspeaks{You can't expect results with no reaction}
    \Mspeaks{Hmm...I guess, the thing is...I'm intoxicated, this girl is too much for me. So I may or may not do something, but 
    for now all I can say is...time will tell for what will happen, just wait!}
\end{drama}
\StageDir{\begin{center}
    Lights focussed on M
\end{center}}
\begin{drama}
    \Mspeaks{
        Love is a funny thing, you think you know everything about it, but really you're clueless as you started.
        The thing is, it's sometimes the one you care about the most you try to hide your weaknesses to.
    It's just that I wanted to tell you I'm okay, but as you can tell I locked myself in therapy sessions, trying to get my mind intact, 
    where did I lose it, maybe I need to investigate that. I complained but didn't act, I kept my anger inside me...it killed me!
    Those early days I wrote poem after poem, a factory in my mind making mass products, but now it takes weeks to make a line, 
    so I thought I'd quit. But those early days were coming back, relapsing....sessions happening in my mind....nevermind}
    \Singspeaks{\textit{He thinks as he has second thoughts fueling his anxiety. He tries to understand his situation 
    he locked himself in? Trying to understand psychology with his expirmental ideas, creativity leading to his mania}}

    \Mspeaks{I'm having seconds thoughts about our friendship, thinking it will end, who's telling me? \textit{\%Singers: his second thoughts\%}}
    \OMspeaks{Yeah I'm telling him she's not right for him, trust turning into issues, who's giving him the tissues, guess what it's me, \%gets a tissue and passes to other hand\%
    here you go!}
    \Mspeaks{She's not a bitch that's what I'm telling you! Why do we seem so distant and close at times is still in question to me? I questioned and trying to tell my neighbor right here she's alright!
    My thoughts are spiralling in simulations, I go from calm into a psycho mania with headaches lasting till next month, is my heart beating normal again, 
    I just had a panic attack today, yesterday and tomorrow. I ask my therapist if I'm going through phases of insanity, but he's 
    saying it's all in my mind....well no shit right??? Is all this trouble worth it, an endless loop I see myself going through, 
    but I'm seeing through a tinted window outside because inside I'm not allowed, blocked from my ownself, something is wrong!}
    \OMspeaks{Fucking idiot, I'm trying to speak some sense into him, like look what ended happening to him a few years back
    , he let his guard down and it assaulted him so hard his anxiety got an upgrade, making breathing a problem, grab the inhaler he may have asthma!}
    \Mspeaks{Why don't you shut the fuck up! If we had a weak relationship it would've ended, wouldn't it? If we didn't care about 
    eachother then why were our backs guarded by eachother, explain your logic that's staying stale, pale pain in the ass!}
    \OMspeaks{You say what you want! But don't forget how you started your poems!}
    \Mspeaks{Don't remind me...}
\end{drama}
\scene[Early Days]
\StageDir{
    \begin{center}
        Return lights to normal room setting
    \end{center}
}

\begin{drama}
    \Tspeaks{Do you remember how you first started writing poems?}
    \Mspeaks{Oh weren't those fun, I would write some at home, in the caf or lunch. I just 
    had all these ideas, and they poured into paper}
    \Tspeaks{Well, we are going to talk about the Early Days...}
    \Mspeaks{Do we really have to?}
    \Tspeaks{Please tell me about it...}
    \Mspeaks{I was carrying wasted emotions, given a platter to feast upon, I thought seconds weren't enough,
     I asked what emotion that was, they said depression...well oh shit. Stuck in illusions I didn't want to leave, 
     I fantasized myself into my own oppression, always tired wanting to sleep. The thing is I liked her, incidentally
     getting me to know her better. She became a close friend I trusted, helping me with the hidden slits under my watch, 
     which wrists was it?}
     \Tspeaks{So what happened next?}
     \Mspeaks{I wanted more, a fat guy wanting more sweets, us together? Wouldn't that be neat. I talked 
     about loving her as a sister, yeah a year later....But that I tried multiple times to end our friendship, 
     after multiple rejections, maybe I was looking at the wrong direction? Right? I was avoiding her, because I had trouble handling it. 
     If I goddamn hear that name again I'll lose it! Those early days were to blow off steam, I was a kettle 
     brewing tea constantly, so shut the fuck about them! I'm not proud of them! They're a lil'female pup, a fucking bitch!}
    
     \Tspeaks{Well, don't you think you're being a bit too harsh to yourself?}

     \Mspeaks{Bitch....Yeah a bitch! Because...Because they helped me with my stitches right? Helped my eyes get sight again, 
     yeah what a fucking bitch! A cunt, a little runt on the streets, I was learning how to get back on 
     my feet after hearing his name everyday, you gotta be fucking kidding me! Oh I remember that, those were 
     the early days, somehow those poems were my saving grace, yeah I hate them, but that's because I can't relate to them.}

     \Tspeaks{But you still struggle to tell her the truth don't you? You don't like to worry her 
     don't you?}
     \Mspeaks{When I'm ready to say, I will...anyways she'll probably be the first to know}
     \Tspeaks{Then what about your greatest fear, you're not convinced of her predicament are you?}
     \Mspeaks{I'm not, but thats a conversation we shouldn't need to talk about hopefully}
    
\end{drama}
\StageDir{Solo @ M}
\begin{drama}
    \Mspeaks{I'm guessing my chances of living, depression creeping up in the creeks of my flaws, I'm trying to act flawless but okay is never today. 
    A bitch crying wolf, I'm trying to cry but the only tears dripping is from the people who care about me, 
    they're worried about my well-being, I'm worried about theirs, never considering mine, now I'm illusions, 
    egos mixing up, now I'm hallucinating without the weed that we all need to get a little happy, 
    joint in our own problems, I'm thinking maybe quitting from this is the solution, but now its mission impossible. 
    Please last project take effect in my life, I read poets poem trying to see where I am as a poet.}
\end{drama}
\StageDir{
    \begin{center}
        Hold up a paper, and reads poets poem
    \end{center}}
\begin{drama}
    \Mspeaks{I started writing when I was sad
    Get an idea whenever I felt bad.
    I never really valued myself,
    on behalf of me I dedicate poems to those who showed me my value.
    It was a clue left for me,
    so, I can see...
    that there’s more to me
    and that I have a dream, I can believe!
    I write poems,
    giving my hand freedom to write.
    Endings clashing as my thoughts come to sight,
    I want to show you my talent.
    So, as you read on, I’ll leave you silent...
    I couldn’t believe I am who I am,
    this sleeve this world puts on me makes me want to cry.
    To be deceived, as feelings are twirled, I see the fakes that come at me.
    He who is the one wouldn’t love if loving was the key to money.
    As solidarity mental confinement can leave a man begging on his knees,
    please oh god please as he begs for mercy, but what he can’t see.
    Was the lord and Savior he believed in made him blind?
    That towards all his kindness, god never existed?
    He was always free, but this pain fell to his legs,
    as when he begs it’s for nothing but comfort.
    That kind of sorts kept fucking with his mind,
    it was a sign to him...
    that a poet’s poem can mean a lot, but for you to listen,
    please get in line, fasten your seat belts because the story has only started!}
\end{drama}
\StageDir{TR @ All}
\scene[The Ever-lasting Dream]
\end{document}