\documentclass[12pt, b5paper, oneside]{book}
\title{Trilogy\\\textit{Poems With Personality}}
\author{Mustafif Khan}
\date{}
\usepackage{color}
\usepackage{hyperref}
\hypersetup{
colorlinks=true, % make the links colored
linkcolor=black, % color TOC links in blue
urlcolor=red, % color URLs in red
linktoc=all % 'all' will create links for everything in the TOC
}
\begin{document}
\maketitle
\pagenumbering{arabic}
\newpage
\tableofcontents
\newpage
\section{Author's Note}
When I write poetry, it's like putting a piece of me onto paper, it just feels like it's part of me. This 
is something that coped me out of mental illness, and helped me throughout life. This is going to be almost 
my 4th year doing poetry, and I have written over 144 poems so far. The Trilogy is a book that contains three of my most 
favourite books, and they were so close to each other, I had to put them together. \\The three books were: 
\begin{itemize}
    \item The Sessions 
    \item Alter Ego
    \item Poet's Poems 
\end{itemize}
The Sessions came to be on a what if? When I first did poetry I wrote an anthology, and it ended up myself in guidance. I had to talk to a 
social worker, and I wondered what if I actually went into therapy? This book is also about my struggle of telling someone you 
care about that you're going through problems. In the book you'll hear about relapse, and that's just a term I use to describe depression coming back.
\par Alter Ego is a book all based around Sigmund Freud's Psychoanalytic Theory, I also named it  to act as an "evil me". But in reality it's more of the id of a person's conscious, it is the raw 
emotional, irrational part of the mind, and of course it's heavily inspired my Eminem's Slim Shady. 
\par The Poet's Poem is based around a poem I wrote in the first of poetry for me, it is based on poetic rhyming, 
and gave it a non-thematic purpose.Its really I just wanted to say whatever I want. But the poet's poem was also planned to be called 
Turbulent Troubles 2, so expect Turbulence to be referenced or even in it... 

\chapter{The Sessions}
\%Skit Begin 
\\M: I want...I want to
\\M: I \dots .just \dots want to fucking tell you!
\\M:  \dots .fuck!
\\\%Skit End
%
\\\\How can I say words without doubting myself
\\How can I not think about the consequences that may be involved
\\Not a thorough plan without caution on all ends
\\It's all part of the calculations
\\Hide the evidence of the fact that...
%
\\\\I have depression!
%
\\\\Clinical to the teenagers in our generation
\\Boomers recall it to be non-existent in us
\\Because we didn't fight in a war
\\I mean who are they to talk?
\\Born by horny soldiers after defeating fascist Germany
\\Going off-topic so I don't have to talk about the topic I'm all about
\\I just wished I had someone I can tell all the time
\\Without my anxiety telling me not to trust society
\\I'm scared to tell her
\\I can't fucking do it
\\But why can't I?
%
\\\\You can't!
\\You can never!
\\Never trust her because that was the first mistake you made!
%
\\\\Shut the fuck up!
\\Who did I show my slits to?
\\Tell her my mind was in turbulent thoughts!
\\Afraid of tomorrow's promise!
\\Who was one of the people who helped me recover?
%
\\\\If you recovered then why are we here?
%
\\\\\%Skit Begin 
\\T: Welcome, you will be here for 15 sessions to help you recover
\\T: After your little incident, I hope I can help you
\\\%Skit End 


\newpage
\section{The Session [E]}
\%Skit Begin
\\T: So please tell me what's wrong
\\M: I...I...I...
\\T: You know you can tell me anything
\\T: So please tell me what happened
\\\%Skit End
\\\\I opened a door to the underworld
\\They told me they'd help me
\\I regret it
\\Demons of my past haunting me
\\Sins of mine coming clearer than yesterday's memories
\\Don't call it paranormal until it takes my soul
\\Takes me whole as it swallows
\\Trying to be tranquil when it's getting me shooked
\\Hooked on these ideas slowly eating me
\\Welcome to the session
\\\\\%Skit Begin
\\T: So you feel like you haven't recovered?
\\T: Depression and suicide still in your mind?
\\\%Skit End
\\\\Recovering from suicide but depression still in question
\\Isolated and feeling hated
\\Insecurities are feeling like a melody
\\They sing me a song
\\And I say fuck it to my decision
\\I ain't going to talk to her about it
\\\\\%Skit Begin
\\T: You tend to lie a lot
\\T: Is it because you don't like being honest
\\T: Or are you scared to be?
\\\%Skit End
\\\\Yeah I lie
\\Fucking lie down act like I'm dead
\\So I can get buried in a grave alive
\\A self-defense mechanic
\\Trying to tell but told don't
\\I'm holding back words and they're holding me back
\\Hard to share my vision when I'm the only one seeing it
\\I tell the truth,
\\They're not happy with it
\\I share a lie,
\\They don't notice
\\They find out and ask why I did it
\\I tell them I didn't notice
\\When I forced my mind to forget
\\I swear because I'm insecure
\\I lie because I don't want to show my colours
\\So I said fuck it
\\Now I'm in a session
\\\\\%Skit Begin
\\T: Interesting, very interesting
\\T: Well Mr.Khan this is all the time we have
\\T: See you in the next session
\\\%Skit End 

\newpage
\section{Back Again [E]}
How do I always come back
\\Solve the problems I'm facing again 
\\If I knew everything
\\How come I needed a therapist to help the answers I knew
\\Ah god I don't know why relapse keeps lapsing back
\\Trying to go slow-mo
\\To get more info of what the fuck is going on
\\But now I'm even more clueless than I previously was
\\An emotional mess
\\Maybe I'm Queen B
\\I tend to be drunk in love
\\Trying to be flawless
\\With my own imagination
\\I'm getting creative of how to tell people suicide isn't the answer
\\Just don't be stupid duh
\\Maybe if I wasn't aware I wouldn't be in this place
\\Not write life wishing
\\Who knows what I would come out to be
\\I'm back here again and I don't know what to say
\\I'm still confused about her
\\Like what the fuck
\\How can I be so confused about someone
\\Wrote a whole book of how I struggle to tell her I'm struggling
\\Here it is
\\I'm scared that I'm in trouble...again!
\\I'm scared to bother her
\\But why can't I just understand
\\Friends help each other
\\So why the fuck am I so extra
\\My mind is playing tricks and riddles
\\I'm getting tickled by anxiety
\\I'm finding it funny now
\\Thought I dealt with it
\\The thing is when I use the word recovery
\\It tends to mean temporary
\\Maybe once I stop being stupid
\\I'll be able to get out of this mental confinement 


\newpage
\section{Social Workers [E]}
\%Skit Begin
\\T: Hello, welcome back!
\\T: So I wanted to talk about one of your poems?
\\M: Which one?
\\T: Its in your anthology, Mental Health
\\M: Well whats wrong?
\\T: What do you mean by your own knife?
\\M: I attempted suicide once...
\\M: I was scared, I needed to tell someone
\\T: Tell it to the social workers
\\\%Skit End
%
\\\\Confidentiality ending with suicidal behaviour
\\So why expect me to talk about suicide
\\You see, I have expectations and math makes me stressed
\\As I lied \dots  
\\I avoided the chance to get a professional help with depression
\\Its my problem,they can't help me
\\Math ended up stressing me a lot
\\So I didn't lie
\\They told me to take deep breaths and relax
\\Something I tend to do now
\\Listen to Dre while my eyes closed
\\Learning to really breath in yoga
\\I can say somehow it indirectly helped
\\The fact I feel true happiness without bleeding
\\I call that a recovery
\\So yeah I wrote that
\\I was scared to say something
\\Wrote it in rhymes to tell my teacher
\\I'm scared I might kill myself
\\I became gluten-free
\\I'm choosing to be anorexic
\\Losing 10 pounds in  a month
\\How'd I do it
\\I drank coffee as dinner for a month
\\Confused as hell
\\Accepting there's a hell I belong in
\\I said fuck you to god
\\So yeah I was scared
\\But I'm not scared anymore to say I suffered mental illness
\\To also say it's your choice whether it stays or leaves you
%
\\\\\%Skit Begin
\\T: Well we will check on you
\\M: Fair enough anyways are we done here?
\\T: Yes, good job today
\\\%Skit End 
\newpage
\section{Political Stupidity [E]}
\%Skit Begin
\\T: So when did you start getting into politics
\\M: When I was 10
\\T: How about reading newspapers
\\M: 11
\\T: How do you feel about politics right now
\\M: Politics is being fucking retarded!!!
\\\%Skit End
%
\\\\America is being ran by an orange
\\Fucking closed by the world
\\Break the door hinge
\\They're acting extra terrestrial
\\Get George Lucas
\\Yet another Starwars episode coming along
\\Evil dictators, crumbling economies, wars?
\\This is what I call political stupidity!
%
\\\\\%Skit Begin
\\T: So how about abortion? What are your opinions on it?
\\\%Skit End
%
\\\\Well a person ain't a person until it's born
\\Murder is taking the life of a person
\\If a women can't take of it
\\Why have a baby go through so much trouble
\\If a women got raped
\\Then should this sperm be taped onto her life
\\White people please confirm what murder is?
\\Because yet you complain about it
\\You don't consider innocent bystanders death
\\Murder!
%
\\\\\%Skit Begin
\\T: Well then, I guess my next question is your views on white people?
\\M: Well...
\\\%Skit End
%
\\\\You can't judge a race by some's actions
\\Some live by the idea of superiority
\\When whites population makes them minor
\\Calling negros criminal
\\Fucking fat man
\\Trying to fuck up this world
\\They call Nagasaki
\\Fucking colonists
\\Nazis without a swastika
\\KGB without the secret
\\Problem is, its not only white people
\\Its every person who thinks they are superior
\\Nationalistic ideals
\\That's what I call political stupidity
\newpage
\section{Intoxicated [E]}
\%Skit Begin
\\T: Please tell me, how do you feel when you meet a nice girl you may like?
\\M: Well I kinda feel like  \dots 
\\\%Skit End
%
\\\\I'm intoxicated
\\Excited to meet this person
\\Very nice to meet you,
\\How could I be fated to see you
\\Are you my soul mate?
\\For goodness sake forget it
\\You're probably fake
%
\\\\\%Skit Begin
\\T: I see, you give up quite easily don't you?
\\M: What makes you say that?
\\T: Hmm well tell me more
\\\%Skit End
%
\\\\She's leaving me speechless
\\I feel like I'm going to faint
\\Because I may be falling in love with her
\\Gravity is bringing me down
\\Her beauty is dragging me down
\\Beauty turning into blushes
\\I got a new crush
\\Next thing you know she's just a memory I lost interest in
\\It can be a week or a year
\\But this girl is really nice
\\I got a good feeling about her
%
\\\\\%Skit Begin
\\T: So then, do you try to get a date with her or...
\\\%Skit End
%
\\\\I don't do shit
\\Get depressed in a fantasy I try to live in
\\Not being able to fit in a relationship
\\I complain but the thing is
\\I didn't do anything \dots 
\\I'm hopeless
%
\\\\\%Skit Begin
\\T: You can't expect results with no reaction
\\M: Hmmm \dots I guess
\\\%Skit End
%
\\\\I'm intoxicated
\\This girl is too much for me
\\So I may or may not do something
\\But for now all I can say is
\\Time will tell for what will happen
\\Just wait


\newpage
\section{Early Days [E]}
\%Skit Begin
\\T: Now we are going to talk about something you may not like?
\\M: Doc that's every session, fuck is it?
\\T: Early Days...
\\M: Do we have to?
\\T: Tell me about it
\\\%Skit End
%
\\\\I was carrying wasted emotions
\\Given a platter to feast on
\\I asked what that emotion was
\\They said depression
\\Stucked in illusions I didn't leave
\\I fantasized myself to my own oppression
\\Always tired wanting to sleep
\\I liked her
\\Incidentally getting me to know her better
\\She became a close friend I trusted
\\Helping me with the hidden slits under my watch
\\Which wrist was it?
%
\\\\I wanted more
\\A fat guy wanting more sweets
\\Us together? Wouldn't that be neat
\\I talked about how I ended up loving her as a sister
\\Yeah a year later
\\But that I tried multiple times to end our friendship
\\After multiple rejections
\\Maybe I was looking at the wrong direction
\\Avoiding her
\\Because I had trouble handling it
\\Those early days were to blow off steam
\\So shut the fuck up about them
\\I'm not proud of them
\\They're not a lil'female pup
\\They're a fucking bitch
%
\\\\Bitch
\\Yeah a bitch
\\Because they helped me with my stitches right
\\Helped my eyes get sight again
\\Yeah what a fucking bitch
\\A cunt
\\A little runt on the streets
\\I was learning how to get back on my feet
\\After hearing his name everyday
\\Oh I remember that
\\Those were the early days
\\Somehow those poems were my saving grace
\\Yeah I hate them
\\But that's because I can't relate to them no more
%
\\\\\%Skit Begin
\\T: But you still struggle to tell her the truth don't you?
\\T: You don't like to worry her don't you?
\\M: When I'm ready to say, I will, anyways she'll probably be the first to know
\\T: Then, what about your greatest fear, you're not convinced to her predicament, are you?
\\M: I'm not, but that's a conversation we shouldn't need to talk about hopefully
\\\%Skit End



\newpage
\section{The Ever Lasting Dream [E]}
\%Skit Begin
\\T: Let's talk about it
\\M: If I haven't told her about it what makes you think I'll tell you?
\\T: I won't disagree or find some type of other reason to it
\\M: Fine
\\\%Skit End
%
\\\\I had a dream I wasn't accepted
\\An atheist bisexual bitch
\\Dick or pussy doesn't matter to me
\\I had a dream I was kicked out
\\The dream that became life wishing's underlying base
\\I had a dream my greatest fear came true
\\I felt like a fool to think about it
\\But my paranoia tells me to stay cautious
\\Being careless isn't an option
\\The natural anxiety that pumps me
\\Please tell me how often is your heart beat calm
\\Put your palm on your chest
\\Tell me is it giving you a warning
\\The reason my hand shakes
\\The stress I have of not being accepted
\\Is the environment I live in
\\So let me work my ass off
\\Doesn't matter about the money
\\I just have some stuff to get off my mind
%
\\The thing is I'm not an idiot
\\I've had friends who never heard my side before leaving me
\\Fucking bitches
\\I've had people not accept me
\\I'm not being theoretical when I have results
\\Find a flaw to go nah to you
\\So yeah I tell my subconscious to shut the fuck up!
\\So I can take the stage
\\Give it anxiety and the fears I feel
\\I don't need to talk to someone about this
\\I just need to make sure they shut the fuck up!
\\Its my dream I had to sleep with for 4 years
\\My everlasting dream
%
\\\\\%Skit Begin
\\T: Thank you for sharing, now may I ask, what happens in the dream?
\\M: Shut the fuck up!
\\\%Skit End


\newpage
\section{Twisting Words [E]}
\%Skit Begin
\\T: Mustafif you wrote Last Project, but a week or so after it, you decided to work on two projects?
\\M: Well, I did write I either had to leave it or change my style
\\M: Also \dots a poet may twist his words
\\T: Explain \dots .
\\\%Skit End
%
\\\\Yeah I wrote fucking Last Project
\\The last poems that you'll ever read from me
\\But I lied, that's what I did in recovery and yet again
\\But why put the blame on me?
\\I've been doing this for three years
\\You think it's hard to just stop
\\How can this stupid genius stop talking about being a faggot
\\How can he stop writing about lagging thoughts
\\How can he stop writing the depression he can't stop talking about
\\Repetition getting a competition with the session
\\Therapy asking me why I'm so depressed
\\I say I'm needy and like attention
\\Anything is material for a poet
\\As long as he can twist his words
\\Talking about sex when he's a virgin
\\Just get ideas from the hub
%
\\\\Do you think I would quit for losing shit to write
\\Get me a pen and a compass
\\Slash my wrists to lose the stress
\\Get the blood for the ink
\\Shit
\\Reality can be anything in the creativity of my imaginative mind 
\\As long as the astral's approve
\\The celestials are yours to do how you please
\\As long as you twist your words
\\Get your sword from the stone
\\Be the hero in your world
\\The world of poetry, it can be
\\A place to confront your fears
\\A place to see what makes you happy
\\Check yourself into self-therapy
\\"Can't wait for the next session"
\\Or to talk about the aesthetics of life
\\Poetry is beautiful
\\You just need to twist those words
%
\\\\\%Skit Begin
\\T: I see, like figurative devices and such...
\\M: Exactly, but also just adding some spice in your mix
\\\%Skit End
\newpage
\section{Love Pt Fucking Something [E]}
\%Skit Begin
\\T: So how many girls or guys have you liked?
\\M: 30 something or so...
\\T: Wow, were all your age?
\\M: Same or older ranging from 1 year to 4 or so
\\T: Wow, well care to talk about it
\\M: Fine I'll say fucking something
\\\%Skit Begin
%
\\\\So many parts to talk about beauty
\\Read all while drinking strawberry milk
\\Hmmm Love pt 1 has quite a deep line
\\After pt 3 I lost count
\\There may be 4 or 6, I wouldn't be surprised if it was 7
\\Some never being released, not relevant anymore
\\Mostly when I wasn't talking about her
%
\\\\But a guy craves positivity from someone so much
\\That when a girl is nice and makes him happy he will like her
\\She helped me, I fell in love
\\The other one was nice to talk to
\\Maybe we should get together
%
\\\\It all started by writing about love for strawberry milk
\\If you know you know
\\It was rewritten for her but not originally
\\We don't say who it was really for
\\It was a mistake on my part
\\Too ahead in my romantic mind
\\I forgot about reality
\\She was way out of my league
\\Like shit
%
\\\\You will never know who I really talk about
\\She may he tomorrow's regret
\\Or today's love
\\So beautiful and nice
\\Humor in her speech
\\Professional but casual as well
\\Cute smile, a happy person
\\Well we all laugh at our pain
\\But in the end, we are okay
%
\\\\Love pt fucking something
\\I hope I'm done writing about love
\\But I doubt it
\\A pattern I can't resist to repeat
\\A mistake never being learned from
\\When it comes to love
\\Eh just fuck it
\\Try your best
\\Whatever trying your best is


\newpage
\section{Lossed Motivation [E]}
\%Skit Begin
\\T: How long does it take to write a poem?
\\M: A couple minutes to a few weeks
\\M: Love took a day, Turbulence took 2 weeks
\\T: Interesting, well what causes the difference
\\M: Ideas, structure and motivation
\\\%Skit End
%
\\\\Motivation is on vacation inside me
\\It sleeps as I ponder on reality
\\Subconsciously writing poems
\\Frustrated with words to phrase what I mean
\\Making up words of how malified it is to write poems sometimes
\\A sick joke
\\Stop calling it Ego, oh god
\\Fucking fake bitches right
\\Getting off-topic taking off points in my poems criteria
\\A goal of perfection of my poetic ideals
\\You have no idea
\\Words fighting in an arena
\\What does cute really mean
\\Does attractiveness depend on testosterone levels
\\Or is it psychological
\\Check in an appointment to ask these questions
\\Doc can you help me?
%
\\\\\%Skit Begin
\\T: Well there's different ways to perceive it, but perceiving is psychological so that may answer it
\\T: What happened to talking about motivation?
\\\%Skit End
%
\\\\No energy to say that word
\\Calculus being delayed for an online presence
\\Staying static if only I can be dynamic
\\Writing poems nah I'm stuck in writer's block
\\Trying to get the cat out of the bag
\\Not trying to be an idiot with my idioms
\\I figure using alliteration are also awesome
\\But bees are hiving around these sentences
\\I am feeling sentenced  to death
\\So sent me to death row
\\For speaking my mind in rhymes
\\Crimes against humanity for speaking out loud
\\I'm shouting but no one hears me
\\I scream but silence overtakes their ears
\\My cause not being an actual clause
\\Catch me before my pulse ends with my last words
\\I'm Okay \dots overtaking my endings
\\"Shit get another idea fucking one-liner"
\\So in the end what wrote last project
\\The death of my motivation to write poems
\\Its ending
\\After the session
\\I don't know my position in writing poems
\\Will I continue with skits
\\Or try to hit a different idea
\\Get the criteria to cover the leaves in this branch of words
\\"Shit just write a poem"
\\Fuck you okay, fuck you
\\I will grab a thesaurus to get all the synonyms 
\\To write the same meaning of words
\\Fuck you in a poem
\\Fake bitch
\\My lost in motivation ends when I can say shit that excites me
\\So get me a fucking topic that excites me
%
\\\\\%Skit Begin
\\T: How about religion?
\\M: You got it
\\\%Skit End
\newpage
\section{Lord? [E]}
\%Skit Begin
\\M: You asked for this so here you go!
\\\%Skit End
%
\\\\Sufferings cuffing me when I'm doing nothing
\\Minding my own business
\\But now I see myself kissing some fucking mythical person's ass
\\The fuck!
\\Nah bitch
\\An itch in my mind I'm scratching
\\Existence getting confusing when he's in myths
\\Getting cryptic when there are temples and monuments for someone we haven't met
\\Not accepting the possibility of non-existent
\\Even extra terrestrial is more practical
\\Don't call me a person who hates religion
\\Just don't fucking involve me in your shit
\\Think about how ideologies killed millions
\\Communism already over 40
\\So let's ask about religion
\\Pakistan and India?
\\Middle East?
\\Palestine and Israel?
\\So let's be real you aren't some pure fucking people
\\Oh those people are different
\\Only exception being extremists
\\They just wack
\\If someone told you, you were wrong
\\Would you smack them?
\\Or accept that they have their own idea?
\\I don't care about who your knees are begging to
\\Leave me from that fucker
%
\\\\I don't depend all my hope on some whore
\\He's just fucking us as much as Satan is with our souls
\\Paining cruelty
\\I'm trying to hain from it
\\But I'm getting shit and anxiety
\\Loosen my rope
\\Before you decide to hang the witch
\\The person in mental confinement in a wasted mind
\\"My emotions are always being used anyways"
\\Wasted being cascaded to be descending
\\Begging to be ascending
\\Oh lord please give me mercy
\\He's calling for forgiveness
\\But he isn't being answered
\\Being left in voicemail killed him 
\\Dependance is dangerous when you're too dependant
\\So is it worth being independent
\\Lord?
\newpage
\section{Questions/That Person [E]}
\%Skit Begin
\\T: If you got to say anything, ask anything what would you say to her
\\M: Have you ever thought of ending our friendship, what do you really think of me?
\\T: Is that all?
\\\%Skit End
%
\\\\Have you ever considered leaving our friendship? 
\\Something so special to me, something I tried to fiddle 
\\It's a riddle as I feel stupid to ask 
\\But have you tried to stop caring about this unbalanced emotional mess
\\If so, I wouldn't blame you
\\That person that features in many of my poems 
\\The Hailie to Eminem
\\The Eazy to Dre
\\The Pac to Snoop
\\I have a question I've been meaning to ask
\\Have you ever thought less of me from what I have evalauted so far
\\Will you be mad if I ask you these questions 
%
\\\\I ask what are these feelings 
\\Why am I being less motivated when I'm worried for her wellbeing 
\\Why the fuck should I care about this person 
\\How does her life affect mine 
\\Selfish to selfless 
\\I started caring about you more than me 
\\Shit I started going through problems so I resorted to forgetting 
\\How come love has to be targetted 
\\Embarassed to show my true emotions 
\\I struggle to say you're like a sister to me in real life 
\\I can't say I care about you 
\\I don't know if this is a confession or a breakdown 
\\I'm going through turbulent troubles writing this 
\\Everything coming back when I'm remembering 
\\I struggle to try and talk when I feel like I may be unbalanced again
\\Off the side like a faggot 
\\Can't choose a side so I go Swiss
\\I don't even know what I was doing 
\\I told myself to stop caring or there will be consequences 
\\It isn't a demotion I just \dots 
\\I just didn't know what I was doing 
\\I have a question 
\\If I left how would you remember me 
\\So lost from social aspects I'm losing it 
\\I already lost it a long time ago
\\Fuck
\\I want to tell you my questions 
\\I want to tell you I may be okay 
\\But the problem is
\\I don't know what the fuck I'm saying 

\newpage
\section{Impressed/Time [E]}
\%Skit Begin
\\T: What do you enjoy about writing poems?
\\M: Well I've managed to make memories from them, whether I like them or not they teach me
\\M: Also some old memories are nice to remember
\\T: Interesting anything else
\\M: I impressed myself
\\\%Skit End
%
\\\\I looked at nature while going on a memo
\\Thought I'd make some notes on an anthology
\\I fell in love with it
\\I just wanted to say I'm okay
\\If I was able to tell her I was okay
\\Our friendship would have been easier
\\An incompetent writer deciding its time for writing
\\Not being able to phrase his emotions
\\Trying to get his mind straight and be kind as well
\\Man should've just said fuck you to so many
\\But the reason I was able to write so many poems
\\My lost motivation
\\Was that I lost being able to show my poems to a best friend of mine
\\She loved them
\\Impressed more then from my last
\\Saw my poems mature
\\My self-confidence came back
\\I dedicated Turbulent Troubles to her
\\Upset I didn't add Turbulence in the end
\\I wanted to quit
\\Imagine writing a whole book based off of something and not even having it in it
\\We gotta go back to the classics
\\I enjoy my old poems
\\Nostalgia getting my eyes drippy
\\Man I'm not crying you are
\\I impressed myself by impressing others
\\Whether it was teachers
\\I fucking impressed 'Houn okay
\\I say that's all I need
\\But I miss the old days of showing them at lunch with my poem book
\\How times have changed
\\They remind me I'm not alone
\\That people love me
\\The words went from suicide to recovery
\\I impressed myself being able to talk about my mental health problems
\\Admitting I attempted with my own knife
\\I have nothing more to say to this
\\Except don't be stupid

\newpage
\section{Unarmed Terrorist [E]}
\%Skit Begin
\\M: You know what I hate, how the media portrays Muslims
\\T: As Terrorists, right?
\\M: Yes but more like every Muslim is either an armed or unarmed terrorist
\\M: Like shut the fuck up America is supplying the weapons
\\T: Want to elaborate more \dots 
\\M: Sure
\\\%Skit End
%
\\\\Fox is sucking Trumps cock deep throat
\\This little slut depends on Trump with its authoritarian viewers
\\Why can't a strong leader be smart as well
\\With Trump's health he may die like Stalin with an ache at his heart
\\A narcissist
\\Is it morally good if he died?
\\This orange bastard is fighting common sense in an arena
\\Sat on it and suffocated it to death
\\Either that or he sent it to Epstein to be raped
\\Giving the Saudis more weapons and saying Muslims are dangerous
\\Mosques getting shot, Quebec being a little racist piece of shit
\\Wow god is doing a good job with his children right?
\\An unarmed terrorists having to deal with the medias shit
\\We are powerless against Chinas internment camps
\\South Asia being in debt to China
\\The fuck they gonna do to their best friend?
\\Uighur being treated like a gay Muslim in Saudi Arabia
\\Tortured, maybe hanged, pulled apart by two horses
\\Whatever it means for men to have a swordfight while having sex
\\I ask whats next on the news
%
\\\\\%Skit Begin
\\T: How about the explosion in Beirut
\\M: An unfortunate incident, take a minute of silence for this tragedy
\\\%Skit End
%
\\\\An explosion we wished was exaggerated
\\Being heard from Syria
\\Holy shit
\\But guess what America blamed it on?
\\Terrorists
\\Like holy fucking shit the Middle East war is still happening because of Americans
\\You know what fuck it
\\Ignorant arrogant fuckers won't listen
\\Why say these obvious clues when these idiots don't know what a brain is
%
\\\\\%Skit Begin
\\M: I'm just done today...I'm going
\\T: Come back
\\M: Fuck this
\\\%Skit End 

\newpage
\section{Fucking Bitches [E]}
\%Skit Begin
\\T: So what do you want to talk about today?
\\M: Fucking bitches
\\\%Skit End
%
\\\\Hitch a ride and get the fuck outta here
\\Pulling up to push people around
\\Go get your ass and kick yourself out
\\Fucking bitches
%
\\\\\%Skit Begin
\\T: Well \dots .could you explain
\\\%Skit End
%
\\\\The bitches that think they're the shit
\\Ask a lil' poor boy to shine their shoes
\\For a dime to pay the nickel he owes
\\Pennies are too much to pay a kid
\\Call it volunteer hours
\\Free labor to make carpets in a factory
\\Enjoying those nice Nike shoes
\\I bet the kid who made it wish it was his
\\Soft hands go into hard labor
\\Enough about the poor talk
\\The fucking bitches need their attention
%
\\\\Living in luxury
\\Partying everyday
\\Not worrying about consequences if it only shows in dollars
\\If we both killed ourselves
\\Who would be remembered more
\\The morals or the popularity
\\Compassion only translate to the perspective on by the person in question
\\A slate they carry to show you
\\But its like Carrey's and Mathers beef
\\Who the fuck was really moaning
\\Giving an actual orgasm
\\Whores getting a bunch of men to try out every type of dick
\\Shit
%
\\\\Let's go back to the poor
\\Living in financial distress
\\I remember doing 5 bucks a month
\\Now I'm doing 100 with a job I work my ass off on
\\Dealing with peoples shit
\\Stupidity not knowing taxes exist
\\Like holy-
\\God
%
\\\\\%Skit Begin
\\M: You know what that's it! Okay that's it!
\\T: Whats it?
\\M: I'm fucking done talking about this shit, what the fuck am I gonna do about it
\\M: Go to a bitch and call her greedy or a whore?
\\T: No, no, this is a place to relieve your stress
\\M: Really! Because I'm feeling pretty stressed right now!
\\T: Okay listen here! You got to do 2 more sessions before you're clear
\\M: YOU GOT TO BE F- kidding me 
\\T: Next meeting prepare your discussion
\\\%Skit End 
\newpage
\section{The Discussion [E]}
Man my whole world is changing
\\Changing years of style
\\Adding more characterization
\\Skits hitting therapy sessions I wish I have discussed about
\\A made-up person I'm speaking to
%
\\\\\%Skit Begin
\\T: Mr Khan are you okay?
\\M: I'm okay, just zoned out a bit
\\T: Well anyways about our previous session
\\M: I know I went a bit overboard
\\\%Skit End
%
\\\\Zoning phases bypassing reality
\\Imagination getting creative of how to fuck with my mind
\\Discussions getting hallucinations
\\Is it me or is it getting shady over here?
\\We all have our own darkness
\\"Hello darkness my old friend"
\\Can nightmares end if you can dream
\\Happiness ain't happening now
\\Pushing reality to its limits
\\It's getting crazy in my conscious now
\\I'm told to worry
\\But now I'm told it's all okay
\\Its time to have a discussion but is it to a professional or this therapist
\\He's effective
\\But the only problem is he doesn't exist
%
\\\\\\\%Skit Begin
\\T: Mr Khan can you hear me
\\T: Listen to me, you got to believe what's right and what's wrong
\\T: Don't believe in irrational beliefs
\\M: I \dots I don't know what to think
\\\%Skit End 
\newpage
\section{Habits [E]}
Maybe I should've left the game
\\I was playing
\\But only scoring losses
\\As much as I tried
\\My habits were dragging me down
\\The hell I was keeping myself in was finally taking me
\\Maybe I didn't give up mental illness
\\This sickness allowed me to write poems
\\My inspirations coming from my oppressions
\\Internal conflicts making it into papers
\\I write then recovery came out
\\Made me realize how stupid I was being
\\But then I went behind it's back and relapse came
\\I warned myself, and last project came out
\\The truth is \dots 
\\The sessions came out not only because I struggled to try to ask for help
\\But because I needed help talking about my problems
\\Not a real therapist
\\But to me
\\The help really worked for me 
\newpage
\section{Mystery [E]}
I always asked myself...
\\Why the cute girl who made my world into colors
\\Became so important in my life
\\Appearing and now I'm pondering upon it
\\I still remember all the cringey shit I did when I liked her
\\Confessions in letters
\\Waiting for her at the bus stop
\\Ah shit
\\As much as I hated them, they got us closer
\\Problem is, I always struggled expressing emotions to her
\\Sessions asking why
\\Trying to act like a Catcher in the Rye
\\Keeping the innocent, innocent
\\But I fell off the edge
\\Breakdowns leaving me in turbulent troubles
\\The mystery in who she is boggles me
\\I try to toggle into it
\\From someone I fell in love with
\\To someone I matched the role of sister to
\\But brothers tell sisters their problems
\\Anxiety coming up to me
\\Random jealousy in the mix
\\Overloaded with emotions I say fuck it to the conversation
\\Ended up in sessions
\\I just want to say it
\\I just want to shout it
\\The mystery I'm shrouded with
\\I wish I can clear this fog that hides me away 
\newpage
\section{Last Session [E]}
I got voices in my head telling me what's right and wrong
\\I'm feeling like a ding dong trying to know which knob opens the right door
\\Poor at listening
\\Having to make up a person for all the warnings I tell myself
\\So I can tell him to shut the fuck up
\\Therapy is not going too happily
\\Not wanting memories made to be forgotten remembered
\\Ah shit
\\I'm trying to figure myself out
\\Before I make a decision that goes all out
\\Getting mad at therapy like Nard Dog
\\I feel like punching a wall
%
\\\\Problems pointing problematic flaws in my personality
\\Problems evolving into bigger situations
\\Just tell her!
\\Never!
%
\\\\\%Skit Begin
\\T: Do you remember why you first sent here?
\\M: My attempt
\\T: No, you were scared about it and had to tell someone in your anthology
\\M: Right,that's when I started using poems for coping!
\\\%Skit End
%
\\\\How could I try giving up a passion of mine
\\Suicide becoming a classical nostalgia
\\Give me enough time and a new book will be made about it
\\Last project to the last session
\\Do I really need therapy
\\Stressed about school when I'm mentally unbalanced to it
\\I care about her
\\But I may need to demote this promotion that was nominated
\\I hated caring about people
\\But now I miss people
\\I love them with all my heart
\\Trust them until I go into rust
\\But
\\How long will it last
\\It could be as thin as a thong
\\With more and more fakes
\\Trust is going on a diet
\\Celiac is making it skinny
\\Problems turning into jokes
\\Man my life is so funny, I'm the host of this circus
\\I'm trying to get Pac in my head
\\Turbulent troubles getting me high on mental illnesses
\\Will death be brought by homicide or suicide
\\I'm reading Mustafif and now I'm in the same situation
\\WAKE ME UP
%
\\\\But who am I supposed to be speaking to?
\\The cute girl who made my world go into colors?
\\Be quiet
\\Sshhhh
\\Be quiet
\\Soft speech slows down breakdowns
\\Break down the wall that's blocking me to speak the truth
\\I'm spitting but it's not leaving my mouth
\\I don't know what's happening
\\Reality not being real with all the craziness happening
\\Is Trump real?
\\He looks like a saggy rump
\\A rapist in description
\\His fat ass probably trying to push pussies his way
\\Oh shit
\\Dumb asses trying to get us killed because they can't put on a mask
%
\\\\My mind confusing itself with its own riddles
\\Little to all clueless
\\I hold my hand hoping to remember myself
\\I question who's holding my hand
\\A fish caught in it's own net
\\Am I off topic again?
%
\\\\\%Skit Begin
\\T: You talk a lot don't you?
\\M: Not in enough in some circumstances when needed to
\\T: Tell her the truth why don't you
\\M: Get a lecture nah man
\\T: Haven't those lectures helped you?
\\M: Well \dots 
\\T: Then what's the problem
\\M: I'm scared okay,I'm scared
\\T: About what?
\\\%Skit End
%
\\\\I'm scared about having to talk about the same conversation again
\\Redundancy is becoming my poetic currency
\\I'm currently not sure what to expect
\\Relapse relapsing the times I've fucked up
\\Fuck poems stop writing, fuck!
\\Revealing slits under my watch
\\Do you know what time it is?
%
\\\\\%Skit Begin
\\T: Time to talk to her?
\\\%Skit End
%
\\\\Am I going crazy
\\Schizophrenic needing this imaginary asshole telling me what to do
\\Nash is telling me it's going to be all right 
\\His will breaking out of his own craziness 
\\It's going to be all right, right?
%
\\\\It will never be!
\\Stress will clobber and chew you for dinner!
%
\\\\I'm being feasted upon 
\\Satan having a buffet with the breakdowns I'm experiencing 
\\Stress is becoming a distress I'm trying to push back
\\I'm lacking motivation to share my problems
\\Poems making it so easy
\\But when I say it I only say gibberish
\\Self-therapy getting more dependent
\\Music getting louder to null the voices inside
\\Gotta love the chronic tunes
\\I'm trying to tune these thoughts out of my head
\\Trying to head in the right direction
\\Is my path highlighted
\\Or am I supposed to improvise this?
\\Freestyling becoming native to me
\\But how can I be free
\\If insanity is always behind me!
%
\\\\\%Skit Begin
\\T: You know the answers to your problems, you recovered already
\\M: So why can't I solve them?
\\T: Maybe the problem is you don't want to
\\\%Skit End 

\chapter{Alter Ego}
\section{Fuck it! [E]}
\%Skit Begin 
\\M: I would like to announce my new book, Alter Ego?
\\Public: Well what's it about?
\\M: Psychoanalytic theory and me quitting
\\Public: That's it \dots 
\\M: What do you mean? I worked very hard on this
\\Public: You always try to quit then release a new book, just make your decision!
\\M: You know what, my decision is \dots 
\\Public: What! 
\\\%Skit End
\\Fuck it
\\I have no words to say to the public
\\I rather stay silent like a ninja
\\Stay out of sight
\\Instead of fuckers always bothering me
\\I tried quitting
\\But words mixing with my hidden anger
\\I feel like I just have to say something
%
\\\\So yeah fuck it
\\That's what she's saying when you go insert it
\\Would you like to confirm your purchase?
\\Men are a horny mess
\\If you need any blood
\\Get it from the boner from their penis
\\Just kidding
\\The thing is the word penis sounds disgusting
\\A Soft and squishy word
\\So instead we describe with a nice K
\\Dick!
\\Don't get it?
\\Maybe that's why some choose to do drugs
\\To give the chronics a little trial
\\Some hoodlums trying to act all gangsta
\\Like rap was to make gangsters
\\Never thinking it might've gotten them out of it
\\Fucking dumbasses
\\I got nothing to say to these idiots
\\Middle age women making me feel endangered
\\Because their first option of sitting might give me covid
\\Fuck outta here .
%
\\\\Fuck it
\\I'm trying to find the words of what to say
\\I'm squabbling trying to find them in scrabble
\\I'm dribbling and trying to shoot
\\Going through the net
\\I don't play sports
\\But I think I scored a point
\\So let me point out the mistakes in this world
\\While trying to find the something to say
\\This year's a mess
\\Governments are being a corrupted mess
\\Imagine if all people lived freely in China?
\\Imagine an uncorrupted Lebanon?
\\Imagine a free America?
\\Ghetto motherfuckers!
\\Hidden KKK members!
\\Listening to rap so they know how to say the word that rhymes with jigga
\\Talking about the people from Niger
\\If you know what I mean
\\So yeah let me say something
\\Let's see it will be for now \dots 
\\Fuck it!
\newpage
\section{K not C [E]}
I always wanted to try to act like an MC in poetry
\\To act like I had something no one else did
\\Something in literature I'm good in
\\But I always thought...
\\If I were to up my game how could I?
\\How could I be the leaders of these Khans that MC's connotate as
%
\\\\Hmm \dots how about this
\\K not C because that's no longer me
\\I'm the Master of the Khans
\\The leader leading through the empathy of your shoes
\\But you wish your shoes were mine Because now I'm wearing yours
\\You want your stuff back but now its priced
\\I'm not this boring old poet
\\I got charm
\\I got rhymes that are now scrabbling through your mind
\\I'm trying to be kind, can you ask yourself this
%
\\\\What is more scary?
\\The KKK or CCC
\\K is just more powerful
\\I ain't calling myself a racist
\\Because if I was then sinful perspectives would be for the white people abusing
\\I'm this poet that's writing the poet's poems
\\Are you sitting tight because the line is almost there for you
\\But are you here for me or am I to you
%
\\It's getting confusing when the material this is being written on
\\Is one you can't see
\\It's because its the vision I see
\\The only other to one see this is my alter ego
\\He's too quiet for this poem but wait, for he will come
\\Because if you C me then ask me if I'm oK
\\Don't think I'm aiming to be the MC of poetry
\\No I'm not quitting until I reach the MK
\\So whoever doesn't believe in me, fuck you!
\\I'm the MK of poetry 
\newpage
\section{Beautiful [E]}
I always wanted to let you know you are beautiful
\\For any demon who says otherwise
\\Fuck them and they go to the deepest part of hell!
\\Sorry this mania is making me a maniac
\\Anyways what was I saying again
\\Oh yes
\\You're beautiful
\\A butterfly fluttering its own wings
\\An independent women finding her way in this world
\\Find yourself crude in this cruel world
\\Don't fall in the traps this world has
\\Girls trying to act all thick, sticking out their asses and asking why we looking
\\It's hard to avoid when you seem to want to show it.
\\Don't be stupid like these TikTok idiots
\\I know I'm being overprotective
\\But I can't stop it when I care about people
\\You don't need popularity to be beautiful
\\You don't need to look like an Instagram model
\\You don't need to change to affect my decision
\\The thing is \dots its not even your looks I'm seeing
\\Your personality is all I really care about
\\I don't care about an attractive person if she's an asshole
\\Next time you want to look pretty
\\Ask yourself
\\Is it the makeup?
\\Or is it the personality? 
\newpage
\section{Believe [E]}
\%Skit Begin
\\Public: What are the next steps that you see in your future?
\\M: Next steps? Well I mean \dots try and completely recover
\\Public: Is that all?
\\M: Yes, now please leave me alone!
\\Public: How will you do it, how will you!
\\\%Skit End
%
\\\\I always wanted to ask?
%
\\\\Did you believe in me when the pit fell on me
\\Did you believe in me when quitting was the only option I was considering
\\Not being able to see my own vision
\\Something getting into nothing but redemption
\\My alter ego is telling me otherwise
\\I feel like I have something to redeem, when I never earned anything
\\If I ever earned a nickel for each time I discussed about suicide in my poems
\\I would make something off of poetry
\\A capitalist growing in my mind
\\Why give for free?
%
\\\\I ask do you believe in me?
\\When I get my high off of my inconsistent mania
\\I'm only seeing people worrying for me
\\I'm seeing myself be insane off of thoughts
\\Too into my mind
\\To not see I'm not being seen kindly
\\Fuck!
%
\\I ask do you believe in the stupid genius
\\As I write the poet's poem
\\Were you waiting in line?
\\Did you strap in
\\Or did you let go when I wrote ego
\\Egos taking over my psyche
\\I feel like I'm a moving hypocrite
\\Because I'm only vomiting words I've already said
\\Repetition getting more and more hungry in my career
\\The poet's poem is getting disappointed in my production
\\I only ask
\\If I had something to prove to you
\\If poems were my only thing to worry
\\Only thing in my mind that was running around
\\Do you believe in me? 
\newpage
\section{Recovery [E]}
I'm asking myself if I would like to recover
\\My alter ego is altering my thoughts 
\\Sending me to the alter to pray
\\I ask the lord for help
\\His son has returned for forgiveness but rejected nah
\\I didn't mean to even go back
\\Maybe he wanted me back...
%
\\\\Recovery going temporary because suicide kept coming into my poetry
\\Tomorrow's promise premising in my sleep
\\The sessions showing me the truth I was trying to hide
\\This id trying to take over my ego
\\My rationality becoming irrational
\\How could I be so oblivious to the truth
\\I was distracted, too easily fooled
\\I became soft and my hard spot became too exposed
\\It's like Kim's nude
\\Which one?
%
\\\\I'm asking myself if I can be fine
\\Then he asks me if I want to be?
\\Issues going into tissues
\\Reality is getting too imaginary, I ask...
%
\\\\Do you believe in me with my recovery?
\\Did you ever think how I would be without my mania?
\\How I would be without my quick mood swings?
\\Mentally stable to be unable to socialize
\\I'm just trying to understand the person behind this body
\\My mind so extraordinary
\\Quick to understand
\\Like how I can understand how fucking stupid others are
\\Recovery revealing repetitions
\\Because parts and parts can't reveal I'm a pussy with my problems
\\I'm getting complaints about the words I say
\\Cunts are saying sometimes I go too far with my imagination
\\And yes I do
%
\\\\I think about all the possibilities
\\Erase them so the one I say is the only one
\\Parallel to the unparalleled truth
\\I'm a fucking fool for thinking you understood me
\\Wheres my therapist?
\\It's time for another session
\\I'm getting crammed as my conscious is getting too full
\\Recovery trying to reveal a new something
\\So something is trying to say one thing
\\Recovery will soon be permanent
\\And when it does
\\I will the best poet who ever lived
\\The MK of poetry to be exact 
\newpage
\section{Nice}
I'm trying to act all nice to all my problems
\\Just smiling and waving
\\I'm crying and sobbing
\\None of the tears are dissolving
\\Because I'm trying to resolve all of this anger into poems
\\I'm getting upset \dots just be nice
\\Just be Mustafif
\\Act like an acoustic with no lyrics
\\I can't speak when all I want to do is scream my heart out
\\But it feels out
\\My alter ego
\\He's telling me to get out
\\But now I can't shout
\\Sleep paralysis getting me in a static mode
\\My brain is lagging to my lagging thoughts
\\I'm trying to be nice
\\No swearing because I'm just so innocent
\\No sex in my thoughts, just flowers
\\I'm a coward who can't say his problems
\\Nice to try and hide my problems in a bowl of icing
\\Trying to be all perfect when I'm the most flawed one
\\I'm talking to myself and asking for help
\\If I really needed help, the sessions part 2 would have comed out
\\My heart is racing it's own marathon out
\\I'm exhausted, breathing heavily
\\Better get me a cup of tea before I freak out
\\The only clean poem because I'm trying to be all nice
\\But that just isn't me
\\Get ready for my alter ego
\\His slumber awakes the next poem 
\newpage
\section{Alter Ego [E]}
I want to tell you I'm okay
\\As if today was the best version of me
\\I wish I can see through the tears I'm weeping
\\I wish I could tell you the truth but lying is running through my veins
\\This bigotry will be the end of me
\\This madness has it's own entitity
\\I call it my alter ego
\\He's right behind me, the shadow that chases me
%
\\\\Get this fucker in the van and feed him candy
\\Kidnapping thoughts I'm making him feel insanity in his own memories
\\Altered to perfection
\\I send him to the alter
\\Ask him if he still believes in god
\\"NEVER, STOP IT!"
\\Stop! Stop it!
\\I'm asking for mercy to my own self
\\People looking at me like why this fucker is talking to himself
\\I talk to my therapist, he says relapse is coming back
\\So I checked myself into the sessions
\\A book into a play
\\I'm writing about my own ignorance
\\So I decided to talk to her and tell her my problems
\\Again...
\\If this fucker would be more compliant
\\I would be more at ease in life
\\Doubts are making me want to drown myself
\\Oh fuck!
%
\\\\Six sickening thoughts he feeds me
\\Six, people can be trusted
\\Five, there isn't a margin of error for everything
\\Four, cutting off of social ties doesn't make death easier
\\Three, suicide isn't the answer
\\Two, depression can be recovered from
\\And one, he doesn't need me!
\\I'm the one he relies on
\\Feeding him the answers to his math problems
\\The genius of the stupid genius
\\All this fucker can do is smile and wave
\\I'm the inner core of him
\\The MK of poetry
\\The alter ego is nothing but an illusion
\\I'm the id trying to take over his identity
\\I'm telling him to move the fuck out but now he's pushing back
%
\\\\I would be better off without this ego
\\I'm telling myself its the fucking bitches that ruined my trust
\\It's this world that made me suicidal
\\People addicted to drugs in high school
\\The fact that you need drugs to make you happy
\\Makes you more depressed than I
\\Fucking rather kill myself than do weed
%
\\\\The stupid genius with yet another poem about depression
\\I ask myself if this recovery will happen
\\I tell myself \dots 
\\It will if I want it to
\\Anxiety is becoming less of a problem 
\\More like a small inconvenience
\\Attacks feeling mild
\\Until it makes me want to faint
\\Then that's when I know I need a break
\\Trying to get into rapping bars
\\But not lose my morals in poems
\\Erotica becoming beautiful
\\Because I rather tell a girl she's beautiful than makes me hor-
%
\\Horror stories always telling us about scary experiences
\\This ego is becoming my demon
\\A spirit trying to possess me
\\But now in pushing back
\\Alter ego telling you the flaws in my personality
\\Now I only ask
\\Who's your alter ego? 
\newpage
\section{Message [E]}
I want to send a message
\\Words I want to convey to you
\\My plane crashed
\\Now my last words are in a black box
\\I forgot the message \dots .
%
\\\\Turbulent troubles troubling my psyche
\\I'm trying to speak but I'm stuck
\\A little bit of light in my pathway
\\I try to peek into it
\\A little creak in the pit in which I fell
\\Relapsing getting into my time lapse
\\An hour glass counting the grains
\\I don't have much time left
\\Before depression takes over my mind
\\I'm trying to find true happiness
\\Its not chasing my heart through bitches
\\It's not from love poems about my lonely self
\\It's not about my psychoanalytic beliefs
\\Maybe Freud was telling the truth
\\Maybe he had a point in his wrong theories
\\No experimental evidence
\\Except the experiments I put myself to
\\Figments in my head
\\If I could see them, call me schizophrenic
\\The therapist is trying to reach me
\\Hes trying to help the problem I don't want help for
%
\\\\\%Skit Begin
\\T: Mustafif what's going on! Are you okay?
\\M: I just don't know what to think anymore...
\\T: Please explain, I can't help without getting more of an idea of what's happening
\\M: I'm losing myself to me!
\\T: Please go on further
\\\%Skit End
%
\\\\Two sides on a mirror, each reflection different
\\I'm losing my associations with simulations
\\Craving loneliness
\\I'm looking at a river and its dragging me
\\Drowning myself to death
\\Suicide is getting harder to avoid when the rope is already on
\\My message is coming to the time of death
\\Its coming soon...
\\I must remember before my carcass is 6ft underground
\\Before my body finally goes to the hell it deserves to be in
\\My sins being forgiven by the eternal torture called life
\\C'mon what was it!
%
\\\\\%Skit Begin
\\T: Mustafif are you okay, what's going on with you? What's going in your mind!
\\M: Just let me think! You don't even exist, you're just a voice telling me what she would probably say!
\\T: Figure it yourself then...
\\M: Wait come back!
\\\%Skit End
%
\\\\I can't stand losing the people I care about
\\I can't stand to lose
\\When winning feels so nice doing
\\The poet's poem will never stand to such a challenge
\\Egos and identities fueling poetry
\\Getting cocky is natural for the gender with cocks
\\The stupid genius stands to put his pen down for the last time
\\Last project getting more and more in my mind
\\My message is
\\I'm done talking when nothing is being heard
\\Sometimes talking to others is more lonely than with yourself
\\When they aren't listening
\\Loneliness crippling confidence
\\But this is confidential
\\So we say fuck it to therapy
\\The sessions is catching up
\\Turbulent troubles talking about egos
\\I'm looking into sinful perspectives
\\Because alter ego is taking over something
\\I don't know what to say except we are all screwed
\\Fuck you
\\Fuck toxic waste known as gossip bitches
\\I'm hitching a ride with an emotional drive
\\Mood swings going left to right
\\Who's right at this point
\\Points being left behind
\\I'm trying to figure what the fuck I'm gonna say
\\Trying to make my poetry unique
\\I'm not sure if my body is related to my thesis anymore
\\Now I'm teething my words to the person who sees me dead
\\I say \dots 
\\The message, I can't decode it
\\Till tomorrow's promise passes me 
\newpage
\chapter{Poet's Poems}
\section{A Long Time Ago}
A long time ago I started writing poems
\\From words in my mind
\\They started going on for pages and pages
\\Trying to make a story out of these rhymes
\\They all started adding up
\\A long time ago, I started writing poems
\\Days and days writing like a mass-producing machine
\\Inspiration and motivation coming so easily obtained
\\Because depression was so evident
\\My poems going on for what felt like years
\\I didn't want to stop talking
\\Now I'm feeling stuck
\\But more free than ever
\\The poet's poems are coming back
\\Just like before 
\\A long time ago
\newpage
\section{Something [E]}
Something coming from nothing
\\I'm asking myself questions that are coming from my mind
\\But nothing comes to mind so I act kindly with a smile and nod
\\I ask what's the next thing coming for me in poetry
\\What's the story I would present to the tomorrow
\\Will it be another story about my suicidal conquest
\\Or about the end of it with a recovery that's sums it all
\\I ask what's after the sessions when I finally talk about therapy
\\Wheres my dignity going to leave me
\\Will it leave me with no virginity
\\Who knows
\\The future is its own adventure slowly unraveling
\\I'm trying to ask what's else is there
\\What's happening after if
\\What if I quit poetry
\\Fucking give up on this shit
\\Leaving it all up to my motivation - inspiration
\\Because life is just an equation we are trying to solve
\\As I think about my next thought
\\I leave you reading about something 
\newpage
\section{I Wonder [E]}
I always wonder if I didn't have turbulent troubles where I'd be
\\I always wondered if the events that happened in my life didn't align
\\I always wonder what lessons I would be given if I wasn't given the pain to learn it
\\I always wonder \dots 
\\What if I never wrote poetry
%
\\\\Poetry being a form I express myself in
\\Hello, I'm Mustafif Khan
\\I'm writing the poet's poems
\\The best collection out of all the poems I've written so far
\\I'm upping my game so I can be the MK,
\\Master of Khans
\\A leader of a leader, how much  power can I try to achieve
\\I wonder if I didn't make the friends I did where I would be
\\If I chose to be with fake bitches
\\I'm giving less of a shit to what I say because I don't plan on caring anymore
\\You can hate me and I'll just shrug
\\Ain't my problem
\\Actually if you hate me, expect to be in my next poem book
\\Because I really don't give a shit
%
\\\\I wonder...
\\What if I had to be accepted by everybody
\\A voodoo doll controlling me
\\It's hanging from the ceiling
\\Oh please give me mercy, peer pressure is fucking me up
\\It's like a dad with the hot babysitter
\\We know who she's really taking care of
\\Trying to not be objective
\\But people just want to be a hoe now
\\Just stop being so open about your horniness
\\I wonder if I stayed innocent how out of it I would be
\\I wonder if I didn't write I'm okay
\\If I would be
\\I wonder if I didn't tell a lie, if I would be honest to you now
\\I'm wondering but now I'm at a conclusion
\\That if my life didn't align that it had
\\Then that scoliosis would fuck me up
\\For all the pain I went through
\\All the turbulent troubles
\\Was to fix me up for the future
\\Mistakes teaching me lessons I'm being tested on
\\Give me the fucking exam
\\I've been studying my whole life
\\I've been wondering my whole life how it would turn out
\\Turns out \dots ..I no longer relate to turbulent troubles anymore 
\newpage
\section{Blessed}
My name is Mustafif Khan
\\And I'm blessed in life
\\Lucky to have the family and friends I have
\\I forget why I was depressed in life
\\I went through suicidal behaviour early in life
\\I'm glad I did as it made me value myself
\\I feel blessed because I know what's right and wrong
\\For my sight in reality isn't disillusioned by the illusions I was casting on my eyes
\\I see the truth and brutality of reality
\\But instead of running, Iface it head-on
\\I feel blessed for the people I decide to surround myself with
\\Love is a strong emotion we don't know much of
\\One thing I know about it is...
\\It made my life a blessing to live in 
\newpage
\section{Doc Talk (Skit)}
T: So what brings you here in today?
\\M: If I'm happy then why do I have trouble believing it
\\T: Well if you were in a constant state of negativity, then you aren't used to the change of mentality
\\M: Well how do I adjust to this positive state
\\T: Well, you got to just smile every once in a while, joke around and be a little chill backed
\\M: Hmmm okay, I'll give it a shot 
\section{Ask}
I ask what's happening
\\Nothing to do with their happiness
\\Sadness has taken over their minds
\\Nothing too kind
\\I ask hey do you need any help
\\Nothing to understand, so I say welp
\\They act like a piece of a lonely fish
\\Do you need help swimming
\\Or is nothing going on?
\\I only ask to make sure
\\But nothing is sure for itself
\\Errors all around something so perfect
\\We can only sum up what's integral to us
\\So I only ask
\\What's integral to you? 
\newpage
\section{Remember [E]}
Remember when times were simpler
\\We got each other shoes when we were in trouble
\\But then you became a bastard
\\Then I thought to myself how I got to be friends with this asshole
\\I believed in you but now you're one of the bitches I hate with my guts
\\Because their spilling out when I cut myself at the stomach
\\Get rid of celiac by myself
\\Yeah fuck it I'm done waiting for a cure
\\I'm lured to believe in dreams
\\Because if you don't have any you're living a life with nightmares
\\Remember when suicide used to tremble me
\\But now its trembling beneath me
\\My ego stronger than my id
\\You can say I know how to identify myself
\\And its definitely not someone who's with assholes
\\Because I have dignity unlike your non existent virginity
\\Cunt that's all I got to say
\\I'm trying to fix my problems with a wrench not a wench
\\I'm not trying to be rude
\\But it's kind of hard to avoid when it's so true
\\That this crude behavior is getting me so high on synonyms
\\Sprinkle some cinnamon on this cinnamon bun that's so sweet to eat
\\Digest the words I'm saying because I don't really know how it's going to sound in your mind
\\But it sounds so nice in mine
\\So just remember one thing
\\When you left, I didnt turn back
\newpage
\section{Lost and Found [E]}
A useless fucking shit
\\A faggot ready to die
\\Should I even bother getting up
\\Lie down, fucking ready to die
\\Nothing to cry about
\\How could I not shout?
\\When I'm buried 6ft alive
%
\\\\Wait what the fuck
\\Mustafif! What are you saying?
\\I don't know! My mind is lagging
\\Sagging on overtalked thoughts
\\I'm losing control
\\These thoughts are dragging me down
\\I'm a useless facking shit...
%
\\\\Wait its fucking \dots 
\\These thoughts are fucking with me
\\Raped by suicide
\\I can't hide cuts, expose them like a slut
\\I hate to admit it, but I'm lost
\\My anxiety is like a roller coaster
\\It's fucking accelerating
\\I'm at a position I may be able to differentiate myself
\\Running from emotion to emotion
\\A crash course for a breakdown
\\I think I'm starting to get it
%
\\\\I can only frown, this is tiring me
\\Let me lie down
\\Lost in emotions, help me before I'm
\\Before...
\\Before I'm \dots I'm something
\\I'm stuck on this word...
\\Wait!
\\It's stuck, I'm fucking stuck help me
\\Find me before I'm lost in my own insanity
\\Laughing like a maniac is my new form of entertainment
\\Help me before I find maggots in my head
\\Lead from a bullet
\\A shovel beside a hole
\\I'm starting to feel cold
\\My thoughts are staring to go frozen
\\Lagging in thoughts
\\I'm running like a windows computer
%
\\\\Did I already say I'm missing?
\\Kidnapped in my own insanity?
%
\\\\Sanity is a necessity
\\Boring! I rather be scoring with million of ideas
\\Craziness is an adventure
\\I'm packing my bags, ready to leave any minute
\\Normality is a social construct
\\Insanity doesn't exist
\\Superficial, artificial, crucial
\\I'm lost because I can't find my home
\\I don't know where I'm from
\\Am I a boy or girl
\\A pussy in life or a dick to others
\\I'm kinda sure I don't have a vagina
\\Lost in uncertainties
\\I'm certain of it
\\Because being blue bounces bullshit
\\Nothing to be agreed
\\Polar thoughts, an alter ego
\\A fucking slim shady!
\\My memories are fading
\\Today I may be lost
\\Tomorrow I may be found
\\But if not \dots 
\\Then I've sought to see tomorrow's promise 
\newpage 
\section{Turbulently Troubled}
It's getting troubling in here
\\I ask if I'm worthy to be in the presence to myself
\\After all the mistakes and errors I've made
\\Can he forgive me
\\For as I grow older, so does my lessons
\\I can still remember dealing with the grief that stroked me
\\I can still remember when my life turned upside down
\\It's when my plane crashed on me
\\The time my message went into a black box
\\Something to speak for me
\\I wanted to stay silent
\\The silent killer was my own thoughts
\\Cuts on my wrists turned into a fashion of satisfaction
\\I wished I didn't have it as an addiction
\\The more I did, the more I learned of the perfect pressure
\\I pressured myself to torture myself in my dreams
\\I was different so why not prepare for abandonment
\\I'm trying to figure out my own proposition
\\My own proposal to my pain
\\As aid hid in my thoughts
\\I locked myself up and when I thought I wanted it
\\It fucked me up now I can only test you to see if I trust you
\\But these tests left you with less trust towards me
\\I ask you for forgiveness as I didn't know what was happening
\\I was distracted by myself
\\I don't forgive myself
\\I can't forgive the turbulently troubled thoughts 
\newpage
\section{The Interview (Skit)}
Interviewer: If you got to say something to the public, what would it be?
\\M: I mean I'm not sure, I mean stay well?
\\Interviewer: Anything about mental wellbeing?
\\M: If suicide is your only answers, then you've barely have been looking at answers!
\\Interviewer: Well said, well this concludes our interview
\newpage
\section{Trust Me and You [E]}
I never wrote poems to encourage suicidal actions
\\I never wrote turbulent troubles to say god didn't exist
\\I never wrote to tell people they are wrong
\\I always wanted to express the opinion never speaking
\\The artistic side of me painting with words
\\I always wanted to say suicide wasn't the way
\\Tomorrow's promise shouldn't be the tomorrow you should be sleeping to
\\I'm asking you to wake up but when I'm holding your arm
\\Its covered with blood from cuts
\\I'm crying, freaking out of what's happening
\\Anxiety racing my heart to the extremes
\\I'm shouting but it's not being heard
\\I'm trying but it seems to not be enough
\\My tears are dripping, I'm dropping on the floor
\\Fuck!
\\If suicide were to happen I wouldn't know what I would do
\\It took me years to find my happiness
\\I'm not saying its quick but time finds it's way
\\Trust me, you need to...
\\Love yourself
\\Believe in yourself
\\And most importantly trust yourself 
\newpage
\section{Next Day [E]}
They say the next day will be better than the last one
\\Bullshit
\\People are giving you shit for the crap you give
\\Sometimes people's goal is to ruin your day
\\A Monday possessed in a person
\\No more boomer talk except we can't sound like them
\\Until we say our generation is the worst
\\But they got a point
\\We got it too easy now because people have advanced
\\But if we have advanced how come it seems to be going backwards?
\\Kids are choosing to stay in their own Neverland
\\Even as the grow up
\\Their minds aren't evolving
\\They're staying as stupid fucking wenches
\\Cunts are trying to commit suicidal stunts
\\Let see if I'll live if I fall off a roof
\\Let's see how I do in a fight today
\\How about I never shut the fuck up
\\How come I need all this attention
\\A fucking little boy in a  grown-up body
\\It's like they got ADHD in an angry mind
\\I'm trying to figure out me and me is trying to figure out the figuring
\\Too confusing to try and explain
\\So I'll leave it alone for another time
\\Just leave it off
\\Because if it can't be done today
\\Then there's a next day waiting 
\newpage
\section{The Interview Part 2(Skit)}
Interviewer: Well Mustafif, several times you have complained about writer's block in your books, yet 
many of your poems ever produced are in these books. 
\\M: Well, its not production, its ideas, I admit recycling ideas, and I depend on references. The thing is after 
a little frenzy, I'll need another inspiration to get myself motivated again. 
\\Interviewer: I see, well...anything else you would like to say about writer's block?
\\M: Well hmm...ummm \dots ah...I mean...y'know...ummm...
\section{Words [E]}
I'm thinking of words to say
\\But the next day I'm sinking in my own thoughts
\\They are falling crawling to the drawer Where my imagination lives
\\I'm thinking but it leads to nothing
\\It's like telling the government to give us a plan
\\But instead they tell the women to go back to the kitchen
\\Their goal is to go backwards so when we say we want to go forward
\\We end up going to the same spot we were at
\\I'm not advancing to this advancement my ego has placed me on
\\I've given me a trophy that I awarded myself
\\It's true I may be a fool in this
\\But I ain't new, my say sees a cruel fish
\\I'm just trying to swim away from all of this
\\Because too much is happening at once
\\Not once did you try to heed my words
\\When I asked you to
\\Because when I am spitting you're just sitting
\\Like a lazy ass little bitch
\\My stitches on my wrists are starting to get heavy with my watch on
\\Look at the time
\\This poem is still going on
\\But I'm not able to think of the words to make this
\\But never mind about that because I use this to talk to everyone
\\Here's me with no censors because I'm not sensing what's right and wrong anymore
\\It's like wearing a thong in the living room
\\You're living so gives a shit!
\\The words are coming soon to the poet's poems
\\He's developing his best book to be coming out
\\That's because I got the words I want to say
\\They're um a fuck and fuck you
\\I ain't giving a shit
\\Poetry going into nothing but words
\\Because they're going blah blah blah
\\A little la dee da
\\If you're a poet these rhymes are natural to nail
\\Instead you ran out and now you're getting nailed
\\No sex without consent
\\Because no means no
\\So before I leave all I want to ask is: 
\\Are you ready for the poet's poems? 
\newpage
\section{Poet's Poem (Original) [E]}
I started writing when I was sad\\
Get an idea whenever I felt bad\\
I never really valued myself\\ 
On behalf of me I dedicate poems to those who showed me my value\\ 
It was a clue left for me\\ 
So, I can see\\
That theres more to me\\ 
And that I have a dream, I can believe\\ 
I write poems\\ 
Give my hand freedom to write\\ 
Endings clashing as my thoughts come to sight\\ 
I want to show you my talent\\ 
So, as you read on, Ill leave you silent\\ 
I couldnt believe I am who I am\\ 
This sleeve this world puts on me makes me want to cry\\
To be deceived, as feelings are twirled, I see the fakes that come at me\\ 
He who is the one wouldnt love if loving was the key to money\\
As solidarity mental confinement can leave a man begging on his knees\\ 
Please oh god please as he begs for mercy, but what he cant see\\ 
Was the lord and Savior he believed in made him blind\\ 
That towards all his kindness, god never existed\\ 
He was always free, but this pain fell to his legs\\ 
As when he begs its for nothing but comfort\\
That kind of sorts kept fucking with his mind\\ 
It was a sign to him\\
That a poets poem can mean a lot, but for you to listen\\
Please get in line, fasten your seat belts because the story has only started
\newpage
\section{Stupid Genius [E]}
It's the fucking stupid genius
\\Ahead in the next section we all ask the logic in Repulicans 
\\Closet rapists 
\\Because the only thing they're fucking doing 
\\Is their secretary!
\\I'm just saying imprisonment will be as good as Trilogy
\\No idea what I'm saying
\\Just call me a philosophy
\\I have opinions I want to discuss
%
\\\\Let's talk about the waste trash we call this new generation 
\\Fortnite is the only thing running in their mind 
\\It has enough space because it has nothing else
\\I ask why people are doing stupid challenges 
\\It's because they don't have any other challenge in life 
\\So grab a knife and just to do the deed to get some idea of hard life 
\\Suicide has become a joke in a teenage life 
\\A trend that's being followed upon 
\\I ask where's the joke in the blood being spilled 
\\I ask where's the joke in the nightmares that haunted me for years 
\\I ask but they can't answer 
\\I was too ahead of myself 
\\I forgot they can't stay attentive
\\Send them to military so they can get the discipline their parents should've done 
\\"oH My iT Is JuSt AbUsE"
\\Sensitive bitches
\\You just don't know shit 
\\Fucking smack them to their senses 
%
\\\\The stupid genius I got that name 
\\Because as smart I am, I can make the stupid choices 
\\You can say it's a mistake 
\\But I call it a lesson 
\\Teach me the next section so I can prepapre myself 
\\Too slow bitches
\\Give me the controls and I'll show you how it's done 
\\The stupid genius giving his lecture
\\The professor dream because learning is his passion 
\\Poetry is all about learning from your past work 
\\I ask if I'm Okay
\\I ask if recovery has been working 
\\I ask because asking has no consequences
\\Every action has a price 
\\But asking is the freebie because we are the curious species 
\\We try and ask all the questions possible
\\Then we look at the impossible and convert it to our understanding 
\\So now the impossible is possible in our own perspective 
\\Burn it up we can find our way back again
\\The stupid genius talks about the blessing of science 
\\The only stupid thing in this poem is those who don't believe in its reality 


\newpage
\section{Republicans [E]}
The minorities are being oppressed by Republicans
\\I ask do I have Pac in my head
\\He's been warning us about this even when he's dead
\\Street violence and drug problems
\\A consequence of the government's ignorance
\\Give everyone their rights because they should already have it
\\Now we ask what's your plan on replacing Obama care
\\He says he's got a better plan
\\His plan is \dots 
\\Rely on Gods plan because he doesn't plan on doing shit
\\Trump will be fucking our corpse
\\Because as long as it's on the earth
\\He will want to fuck it
\\Republicans are closet perverts
\\Not the one who are lowkey they like tits and asses
\\No they're the ones who rape their secretaries in the closet
\\If they didn't they'd have to go to other ways of dealing with their boners
\\Gaining power from dead black bodies
\\The police are their minions
\\The hitmen in the law
\\White people acting superior when they're the minorities
\\Acting defensively they retaliate by fucking us over
\\So to these nationalistic assholes
\\I welcome you to hell where you definitely belong
\\Even Satan is afraid of you
\\Not because of anything with strengths
\\But how fucking stupid you are 
\newpage
\section{Silent [E]}
Talk slow and steady 
\\If you don't keep your hands steady on the wheels
\\He'll pull you out 
\\Push you against the car 
\\Put the cuffs, even if you have rights 
\\Innocent to the bone 
\\In the eyes of the laws
\\Your colour is what makes you a criminal
\\They tell you to shut the fuck up
\\"Stay silent you fucking minority!"
%
\\\\Oppression being solved by opioids 
\\No more pain when your thoughts aren't yours anymore
\\Selling drugs because it's the only option 
\\Even welfare is too rich for you to get 
\\The depression leading to tomorrow's promise 
\\We ask \dots how do we fix this?
\\They say, we got a plan 
\\Get more cops to fuck you up!
%
\\\\Arrests with no reason 
\\Racism is getting people innocents raped with no questions 
\\Because as long as you have colour, the penis can enter anywhere 
\\Fuck condoms do it raw 
\\They saw all lives matter 
\\Then what about Trump's or Hitler's?
\\I say if you have logic 
\\We ask to help the people who needs help the most 
\\Something that should've been fixed a long time ago 
\\But now time is still going on and nothing has been changed 
\\Because even Obama wasn't able to help 
%
\\\\We preech but no one is listening 
\\We ask what we said 
\\It's like asking the kid in the class what the teacher said 
\\He doesn't know shit because he wasn't paying attention 
\\Now he says the problem isn't necessary 
\\I ask what's more necessary
\\Money or lives 
\\Nothing about right or left 
\\But a moral question 
\\Because if you said money 
\\Then can we arrest you for fucking murder 
\\I ask if the cops heard when he said he couldn't breath
\\Repetitions as he's struck on the floor by a knee
\\We take a knee and pray for people's protection 
\\Corruption leading to monsters 
\\How can we trust the law enforcement after these murders 
\\More need of social workers dealing with people's trauma 
%
\\\\Mosques being shot because some Arabs are fucking our image 
\\But no one is complaining that Americans are locking up children 
\\Or how Canada is still discriminating the First Nations 
\\They're choosing pipes rather than them 
\\Economy is more important than the lively innocents 
\\Black Lives Matter because they need our help more than ever 
\\I want to help my own way 
\\I'm doing what I do best
\\Writing poems about the imprisonment of others 
\\We are being silenced in our own mental confinement
\\Send me to the detention for re-education if I'm speaking too much
\\I got words and I have a platform 
\\Now they're going together against the silence of minorities
\\So I speak against these racists 
\\Because fuck those little cunts 
\\Staying silent is yesterdays motto 
\\Today's motto is speak your heart out against these motherfuckers
\newpage
\section{Another Poem [E]}
Another poem about stupid mother fuckers
\\Trump has Corona
\\Gets what he wants, will America be serious
\\Will anyone be?
\\I'm not dating until someone takes me seriously
\\Because at this point I'm trusting my instincts instead of others
\\I don't have anything against people
\\Except that, well they're people
\\Complex creatures
\\Psychology is struggling to explain how stupid people have become
\\Video games, technology
\\How about we are being easy on these fuckers
%
\\\\Like oh my god like I can't like wait to play Fortnite
\\Trolling children, overdramatic brats
\\Parents better start disciplining before I smack this fucker
\\Actions come with consequences understand that
\\Nothing comes for free unless you're a cheeky person like me
\\Everyone is preferring these fake thick ass girls
\\If Kylie showed her brain more than her ass
\\Maybe her fans can get grades that don't mean they're failing
\\Self-conscious about what I need to wear next
\\I'm sorry but I don't care as much as you do
\\So sorry that I'm not wasting my time
\\A nice plain t-shirt from George is all I need
\\I don't need to waste money on looking something I'm not
%
\\\\Dumbasses not paying attention to school
\\Call themselves flat earthers
\\Go on TikTok and commit suicidal challenges
\\Oh it's for the viewers
\\Let me overdose
\\Have a hard time breathing
\\Get Trump an inhaler
\\Then me, anxiety is getting on my mind
\\A puff used to get off it because I thought asthma took my lungs
\\Accidental uses
\\Another poem let's see
\\The poet poems is judging my work
\\Is this rhyming enough
\\Am I in spirit with my vanguard in Cray
\\In the shadow realm, I lost a duel with Yugi
\\The Pharoah is showing me the heart of the cards
\\Now I'm drawing the next card of life
\\Will it be another case of relapse
\\Locked up in the sessions again
\\No \dots .
\\Its enjoying poems again
\\Another poem to remind me
\\One of the loves of my life
\\The poems that take the words out of my mouth 
\newpage
\section{I Have a Dream}
I got a dream that politics would be a lot smarter than it is
\\I have a liberal democratic dream
\\Not the eternal one that tortured me for years
\\I have a dream that anything was possible as long as you can put your finger on it
\\I had a dream suicide wasn't a problem anymore
\\That people learned that we love them and asked them to stay with us
\\I have a dream I wish would be true
%
\\\\I pray for the minorities to deal with this majority being abusive
\\An abusive marriage and when the cops get called
\\They start shooting the innocents and say they are terrorists
\\I ask why life is being a stab in the back with its knife
\\A sharp blade injected
\\I pray for mercy and its not being granted to the ones that need it
\\I have a dream people would understand why black lives matter mean
\\It's quite obvious all lives are equal
\\But its goal is to help the ones who need it the most right now
\\Because if a 5-year-old being arrested isn't cruel
\\Then I'll call you a KKK member
\\Go ahead whole that cross
\\I have a dream extremists wouldn't exist
\\I only wish the best for everyone
\\I have a dream
\\The words I say in these poems would be considered 
\newpage
\section{China [E]}
China...
%
\\\\A country I adored since my childhood
\\The country who dared challenge Genghis
\\From Song to Yuan
\\The Mongolians brought a golden age
\\But now we are at a controversial spot with you
\\Citizens freedom, covid 19
\\I ask what's happening?
%
\\\\Let's be honest, there is no government more efficient than China's
\\There's no mistake a dictatorship is faster
\\But you're trying to commit genocide on your ancient enemies
\\The Uighur from the Leo Dynasty
\\I ask if they're going to be free
\\I ask if there is anyone we can do for them
\\Unless you're ready for war, I don't see another option
\\You can post awareness on Instagram
\\But what's it going to do
\\It ain't going to reach the Chinese
\\It ain't going to change shit
\\What! Are you expecting Muslim countries to do something?
\\Most in debt to the titanic country, they wouldn't fuck with their best friend
\\So I ask what's happening
\\It's quite simple
\\China doesn't want to share their country anymore
\\They want it all
\\As much as it hurts
\\What's there to do?
\\Now you think they are so bad, but they aren't that different
\\What about Canada with first nations?
\\What about America with African-Americans?
\\History is just repeating itself
\\This time we are witnessing it
%
\\\\So we ask...
\\China whatcha tryna do?
\\People are blaming you for covid!
\\Whether its natural or human made
\\It came from Wuhan
\\But harassing innocents
\\That's fucking ridiculous
%
\\Here's the thing \dots they appropriated by trying to contain the city
\\When it became a pandemic, it was up to the country
\\And when it came to America
\\They're trying to rely on Regeneron
\\Because Trump had it injected in him
\\The thing is...
\\I'm not defending their actions
\\I'm not saying it's okay
\\But here's my question?
\\If journalism is banned in China
\\How are people getting news in Xinjiang?
\\If the Mongols fought in the Xin Empire
\\What did Mulan do wrong?
\\The thing is, everything can be controversial if there's another side to it
\\The problem is, for those unaware of politics
\\You can't change shit without a majority side
\\When it comes to China \dots 
\\You aren't even a percentage 
\newpage
\section{I Got Questions [E]}
I got questions leaving my mind in an instant
\\Curious to the curiosity humanity is leading
\\My mind is trying to unravel the novel that's making us so worried
\\The catcher in the rye is telling me to not worry anymore
\\I got questions, how do I leave the field of rye?
\\Tell me, tell me!
\\I got questions but they're trying to eat me
\\It's going tick and tock around Neverland
\\My thoughts are tictoc and I'm hook
\\They're making me afraid
\\I'm questioning myself answers I don't know but now it's an interrogation
\\TELL ME WHAT I NEED TO KNOW
\\I told you I don't know anything
\\Get this person out of my sight, next bring in the therapist
\\Mustafif what's happening, what are you doing?
\\I got questions and it's now taking over my mind
\\I'm trying to think but now my thoughts are clinging and cloning exponentially
\\I'm zoning out of reality to try and figure out my own psychology
\\It's a mess and now it's about time for a breakdown if my calculations is right
\\I'm holding tight to myself but I'm losing it
\\Bring Alter Ego next
\\We are done talking
%
\\\\The fuck you want little pussy ass bitch
\\This is the time suicide wants to kill itself
\\Depression is just an oppression for the weak minded
\\I'm trying to be kind to myself
\\But cuts are leading to being otherwise
\\I got questions
\\Like what makes you become suicidal
\\I wrote the poet's poem now I'm here trying to answer my own curiosity
\\Why did I want to die
\\I ask myself that every day
\\Was it because I didn't value myself
\\A sad sob being a little pussy
\\Or was it something more
\\I don't want to give it more thought
\\If so I would make the sessions part 2 for another time of relapse
\\I'm trying to figure myself out before I run out of ideas
\\Because if you gave me energy then I would have strength to do something
\\If I wasn't starving myself then I wouldn't be here asking questions 
\newpage
\section{Gaze}
This gaze is leaving me speechless
\\Clueless to what my hormones are tricking me in 
\\All I see is beauty in her eyes and as she smiles
\\I'm a magnet that's too attracted 
\\I'm trying to walk away 
\\But I'm walking backwards 
\\I'm going back so I can fully understand what's taking me 
\\This gaze is leaving me speechless 
\\Her beauty is too much for me 
\newpage
\section{Lovely}
Isn't she lovely
\\Dazzled by her glamorous appearance
\\I an appearing blushed to this crush I have been interested in
\\Lovely to this lovely ma'am, nice to be in service to you
\\Nice to meet you
\\I ask if I'm good enough to be in your presence
\\This coded word
\\That emotion is leaving me in self doubt
\\My self conscious is acting up
\\I'm acting all shy to this no confidence man standing here
\\I'm falling in dream of the if or the may be
\\Your hair twirls around my mind
\\It's like the night sky going to sunrise
\\I'm waking up but when I see you it's like a dream
\\I'm day dreaming a future not behold to be true
\\Living in a false reality
\\A toxic material burning through my mind
\\I need time trying to see through these illusions trapping me
\\But for now
\\I say...
\\You sure are lovely 
\newpage
\section{You}
Who are you?
\\To be so beautiful that my eyes can't stop looking 
\\I'm trying to look away 
\\But I just go back
\\Temptations making me creepy of where my eyes are going 
\\No no...look away 
\\Now they're back at the real focus 
\\A beautiful smile, a nice personality 
\\You put love and me in the same aisle
\\I'm shopping but you're the only thing I need 
\\Everything else just seems shit without you 
\\So now I ask what do I do to talk with your majesty in my imagination 
\\I'm not sure how to say this
\\But this is yet another tragic story about my anticlimatic endings 
\\Maybe not this time
\\I'll get your insta and we'll be chatting 
\\Getting to know each other 
\\Then I'll make my decisions off of my criteria 
\\Hmm, check, check, check
\\Check this out, in my mind you're perfect for me 
\\Theoretical messing with the experimental
\\The only experiments I want is you and me 
\\Together we get a reaction that means success 
\\Me and You are too good to be honeymooned 
\\My illusions are trying to catch up with my ambitions 
\\When I see you 
\\I can't see any more clearer
\\As time does its job 
\\I will do mine 
\\Asking you to be in my future
\newpage
\section{Waiting}
I wait for a chance for something 
\\I always ask if I had the chance would I take it 
\\Shoot the shots you're given 
\\But now it's me being shot but no one is shooting 
\\I'm waiting for a valentine 
\\But now I'm buying myself a card and chocolates
\\I wait for a chance to be with someone 
\\Trying to get the perfect girl
\\But I never thought about presenting the best me 
\\To show her my true potential
\\I ask if its worth trying after each rejection
\\Is it worth the attention after each denial
\\I wait for the answer 
\\Once someone calls back, I'll pick up immediately 
\\But now I'm still waiting 
\\Chasing back my heart
\\My heart is lonely 
\\Stranded in a vast ocean waiting 
\newpage
\section{Trilogy [E]}
\%Skit Begin
\\T: So Mustafif what would you like to talk about this session
\\M: What do I do if I see myself going through relapse again
\\T: You already know the answer to that
\\M: But what if he stops me
\\T: That is something only you can handle, I can only tell you, it's your mind, anything done in it is your doing
\\\%Skit End
%
\\\\I'm asking in the sessions what if my alter ego came back
\\My psychoanalytic perspective is getting a bit too heavy in my mind
\\Because my poems are getting more psychological
\\Get me to a doctor or witness the insanity at its finest
\\I'm just joking
\\I love being overdramatic
\\My illusions are altering my reality
\\My eyes are changing its lenses
\\They're getting a byakyugan and he's entering from my weak point
\\He's getting me weak-minded
\\So I'm begging him to kill me
\\So I grab the knife, the rope
\\And tomorrow's promise is the tomorrow I'm waking up to
\\Trilogy is talking about my mind
\\Because its getting harder to explain 
\\Three chapter are three books
\\But all too similar to be separate
\\Because I went from something to alter ego
\\A planned subscription site
\\To talk about my complicated mind
\\I thought about my choices and now I'm quitting 
\\Oh wait take back my choice 
\\Crumple crumble it up 
\\Throw it in the trash 
\\Now I'm back in this game after Turbulent Troubles
%
\\Complexity is becoming like China's politics
\\Change my reality before they try and erase my history
\\The UN embassy do something you fucking useless shits
\\I'm not done ranting
\\If I was rapping this would be 10 minutes long
\\One song that's as long as Blackpink's EP's
\\Oh yeah fuck them too
\\Because once they got opinions in their music
\\It went all down hill from there
\\They don't know how to make songs
\\They only know how to look pretty, so do me a favor
\\Be models and stop calling yourself artists
\\My poems are just raps without a beat
\\When they do, they'll repeat like how I see 
\\My vision orchestrated but until then 
\\Fuck rap, because at this point people only hit the basis of rhymes
\\They only hit the oasis that's actually as big as an ocean
\\So while you're bobbing, I'm swimming
\\I just don't see the reason I should get into it
\\The difference between poetry and rap
\\Is that rap is for really angry poets
\\I'm just an angry poet
\\So once I get really, all my lyrics will be under a beat
\\They'll go with a little melody
\\With a nice chorus
\\Because I can freestyle better than I can write poems
\\These are coming so easily to me
\\I spent so long talking you forgot this is about alter ego
\\But he was talking all over this
\\Are you confused, well we work together to write these poems
\\A perfect match,all working in one brain cell
\\Because all the other cells are for the rhymes we imprison
\\So give me a reason to quit poetry
\\Give me enough time and another book will come out
\\Taking a break for me
\\Is just time to absorb all my ideas into one entity
\\So I say fuck it sometimes
\\Put three books together
\\Then you get The Fucking Trilogy! 
\newpage
\section{Tomorrow's Promise}
I'm asking if the lord will have mercy on my life
\\For whatever I wake up to, it isn't tomorrow's promise
\\I'm asking if my depression won't be the end of me
\\I'm too young and I have so much to live for
\\But why am I the one telling myself death is the way to go
\\Why am I the one that tells myself if I got a better blade
\\Cutting would be so much easier
\\More precise and clean
\\I'm asking myself if I wore watches to hide cuts if I ever knew what time I had left
\\I didn't know what was right anymore
\\I kept relying on myself leaving loved one worried
\\I'm trying to make an excuse to this
\\But I was selfish
\\How could I do this to them
%
\\\\After confessing in an English assignment
\\The first product of my poetry
\\I was sent to the guidance counselor
\\We had a talk
\\He had to tell my parents the news
\\I asked him if he couldn't
\\"Please sir, please don't "
\\"I'm sorry but this is for safety, it is necessary to do"
\\I left worried to the bones
\\My hand, legs, and mind shaking
\\Never so stressed in my life
\\I talked to her
\\I was freaking out
\\I needed to just talk to someone about this
\\I was freaking out
\\I was being tested the truth at home
\\My mom asking what she did wrong for me to end up like this
\\The guidance counselor told them I had to see a social worker
\\I went but I lied
\\I had to, it wasn't confidential
\\I told her about the stress I get
\\The everlasting inspiration for the sessions
\\What if I told a therapist, a social worker the truth
\\I didn't like how soft she was speaking to me
\\It scared me
\\I was stupid
\\I didn't value myself
\\After poems and poems it made me realize
\\How great I am
\\I ain't a perfect person, but I'm a perfect version of me
\\I'm asking how could I help those with suicidal problems
\\Something that's cracking and crumbling their mind
\\It ain't your thoughts trust me
\\Trust me, you don't think I went through this
\\I get more joy doing what I love than slitting
\\If you killed yourself
\\What made you try to,  what made you do it
\\What aligned wrongly in your life for your path to go this downhill
\\I'm asking because I want to know
\\I can only help with more than I want to kill myself
\\So I'm asking
\\What makes you want to go to tomorrow's promise 
\newpage
\section{Turbulence (Original) [E]}
Emotions couldn't stop any shit of this world's needs
\\It came to the point that weed became
\\People's need that one couldn't fame
\\Without a past with drug problems
\\Columns of arrests with such a stupid thing
\\I'm trying to calculate the logic in this
\\Before you argue let me finish
\\What did I fucking say!
\\Hey! Shut the fuck up
\\Let me share my opinions
\\Because yours is nonsense
\\This world is a hot mess
\\Less dignity in everyone
\\Get yourself together before we all crash
%
\\\\I'll dash through my thoughts
\\Prepare for the mental 9/11
\\I can't believe there's a heaven
\\When this world is becoming hell
\\People's privacy being sold
\\Tell me how low we have went
\\Has god sent us a message at all
\\Of course not
\\That bastard hasn't decided to pick up our call
\\Oh lord all mighty
\\Fuck you, because when I needed you
\\Were you there? No!
\\You let her die
\\And you made me see the amount of pain she was going through
\\Do you know how hard it was to not cry
%
\\\\I struggled to say hi
\\Seeing those oxygen tanks
\\It cranked my tears
\\And were released on that day
\\The worst day in my life
\\The strife I went through
\\I feel like a fool to believe in you
\\When you failed to save her
\\She died from cancer
\\I thought you had the answer for everything
\\You aren't even a thing
\\So fuck you
\\If you do exist
\\Then I rather go to hell than to see you
%
\\\\Life is like an airplane
\\Right now we're crashing
\\The world trade center is coming
\\Brown people was at fault
\\Dumbass wiggas
\\We too busy with the Pakistan-Indian feud
\\Dude why would we fuck with you
\\Talk to your corrupted Saudi allies
\\Or your military ties with Islamophobia
\\I mean why should I complain
\\I'm not a part of Islam
\\I just need to calm down and explain
\\I will always complain about Islamic nationalism
\\I felt restricted in Islam
\\I couldn't deal with their corrupted purity
\\Clarity is hypocritical
\\Comical to white nationalists
%
\\\\Muslims are terrorists
\\Because we fell so low to America's level
\\We became the devil we were told to avoid
\\Muslims stopped helping each other
\\When we helped another is lost in a corrupted void
\\So who care about the Hui in China
\\They are tryna earn their rights
\\But that's against China's tight laws
\\The Hui's are flaws according to China
\\So lock'em up and re-educate them
\\Human rights have now became on option to a government
\\That statement gives this world no dignity
\\Do we even live in reality
\\Does actions have clarity
\\Or does the hierarchy
\\Keep laughing happily
\\Because anarchy is coming soon
%
\\\\Soon our minds will run on cartoons
\\With dumbass comedy from sitcoms
\\From what this has turned us into
\\Give me that needle of morphine
\\Let me die and kill me
\\Stab it into me
\\Let me see very quickly
\\Let me think very quickly
\\I'll laugh hysterically going hee-hee
\\Leave me with my thoughts
\\Before I die from an overdose
\\Oh no that was close
\\Drugs almost got to me
\\It bugs my brain, that ain't for me
%
\\\\I don't want your weed
\\I don't need that shit
\\Cocaine ain't going to make you sane
\\It'll hane you from the law
\\It'll make you hail Mary
\\Let's go to hell already
\\Sorry I forgot to live life steadily
%
\\\\I keep forgetting
\\My mind has so much shit
\\There's no room for anything to fit
\\Hit me I dare you, no don't, please don't
\\I won't go insane, I promise
\\Fuck you, you don't control me
\\Please leave me be, or you'll be next
\\Don't text me back, because I won't either
\\Don't care about me, why do you...please tell me
\\I see
\\I understand
\\How dare you insult me
\\Care about me? What bullshit
\\Come here and I'll hit some sense into you
\\No, I understand. I care about you a lot as well
\\My mind is making me go through hell
\\I love you okay and always will
\\I'm sorry I almost liked her three times
\\Psyched me as if I committed three crimes
\\I'm sorry but I still need to find my purity
\\To see if it even exists in this reality
\\The corruption in me is clouding my mind
\\It's kind of overwhelming
\\It's really helping my intelligence
\\But as it does another voice speaks
\\Its voice teeths into my mind
\\I was blind to it,I can't stop it
\\Thoughts hopping because I was too late
\\I hate this
\\I can end it that was my thought back then
\\End it quickly so let me go to hell
\\Sell my soul to Satan
\\I kept hating myself
\\I wanted to commit suicide
\\I wanted to hide my emotions till it killed me
\\In these nightmares I kept seeing slits all over my arm
\\The harm I did to me gave a satisfaction
\\It was a distraction to my overwhelming voices in my head
\\Instead of correcting my sins I committed my greatest
\\I say the most greatest sin one can do
\\Is make their mother cry
\\How could I have done that
\\I sat in shock of what I did
\\My emotions couldn't be hidden to my mom
\\I sat on the bed with her, seeking forgiveness
\\My last chance was all I needed to make her proud
\\The sound of tears caused by me can't happen again
\\Not again
\\My insanity will benefit this world
\\The horde of thoughts will process everything
\\Anything is possible as long as there is a will
\\One day we will find the way
\\Anyone who decides to cause me pain
\\They will not be sane anymore
\\Tomorrow all regrets will be poured in tears
\\The greatest fears of humanity is losing their ego
\\So let it go, and work with me
\\I'll let you see my plan for the future
\\My own philosophy isn't a culture I follow
\\But is rules that regulate me, so I won't be shallow with you
\\Who doesn't follow their own principles
\\Let me invite you, as we talk in a plane
\\My ideas might sound insane
\\Our conversation might crumble in silence
\\It's not because anything went awkward
\\You might be a coward, but forget that
\\Hold on tight, shut the fuck up and stop screaming!
\\We are crashing, sorry our plane is in turbulence
\\If we both die
\\Tell me one thing
\\If the hinge falls off the door killing us
\\Will you be going to hell with me? 
\newpage
\section{Turbulence 2 (Original)}
Let's go to church
\\While drinking alcohol
\\To ask Jesus 
\\How much sins we're getting
\\I'm starting to feel god hates me 
\\At least we can agree we don't like each other 
\\God isn't my father \dots it's my imaginary devil
\\Let's go to hell together 
%
\\\\The door bursts out of the plane 
\\Do you think my question was insane!
\\Now tell me will you go to hell with me?
\\Would you accept me knowing my sins
\\The fact I overdosed prescriptions 
\\Or that I'm too scared to ask for hugs
\\Fuck! This is how I'll die 
\\I'm not gonna lie, I wanted it to be honerable
\\If I die \dots 
%
\\\\Don't bring my friends to the funeral
\\I won't be able to wipe their tears 
\\My fear is to lose my family
\\The people close to me
\\I'm not going to die from turbulence
\\Let's have another 9/11
\\Instead aim it at me!
\\To fix this broken imperfectionist 
\\Still...if I die
\\I want to tell her that I love her
\\She's has every quality I want in a person 
%\\Someone I love talking to
%\\Someone I want to be close with
%\\If I die!
%\\Can I at least tell her I love her 
\newpage
\section{Turbulence 3 [E]}
I'm wondering if the hinge fell off the plane 
\\Whether sanity was exclusive to know how all of it was feeling
\\If I went to church, would the lord accept me?
\\I have too many questions in the short time turbulence is handing me
\\I want to ask for forgiveness of all my sins
\\But I think about my proposition
\\Noticing the bullshit of its details
\\Why should I regret all the mistakes I have made
\\Regretting everything can make one's sanity insane
\\Drive you to the madness of its wickedness 
\\Imagine a teenager asking for forgiveness after he masturbates
\\We aren't perfect, but asking to be
\\This clarity of purity
\\It's just too flawed to achieve
\\But its whether our right is in the same perspective
\\I'm not seeing your visions
\\So I ask not to be involved 
\\I ask if my poetry has evolved
\\I went from tomorrow's promise to self-therapy trying to fix it
\\Relapsing through the sessions
\\Capturing alter ego and sending him back to the unconscious
\\I ask whether this is my last book
\\Lovely being cancelled due to my mental nature 
\\This book is just quite something 
\\But I have too many ideas to compact
\\But it's location is still a mystery
\\I ask...
\\When I fall out 
\\What will my black box say?
\\What will my last poem be?
\newpage
\section{Poets Poem 2}
Depression shattering my mind
\\I'm trying to pick up the pieces of this puzzle
\\I'm trying to say I'm okay
\\But tomorrow is tomorrow's promise
\\No one lined up so now I'm going through turbulent troubles
\\No one wants to hear my opinions in life
\\I'll grab my knife and commit the deed
\\In the greed of my need for attention
\\I ask please leave me
\\I need attention to me
\\I ask who you are as I am who you are who I am
\\Nothing is making sense
\\I could've said I am you and you are me
\\But none of that matters anymore
\\It's getting psychoanalytic here and this theory is seeming false
\\Freud tell me what's true
\\I'm so confused of what the truth is
\\When the details it entails are all blacked out
\\Because black lives matter
\\I ask does the poet's poems matter
\\The ladder of thoughts are getting me to have a panic attack
\\I'm trying to climb, but the sky isn't the limit anymore 
\\Hold my heart it's getting heavier
\\I'm Frodo and its the ring
\\Kill me I ask
\\Because even when suicide left me
\\When I see a blade, I ask what if
\\What if I scraped it on my wrist
\\How much pressure would it need to cut
\\I mean what if it scraped accidentally
\\A felony in the mental committee of laws and mentality?
\\I ask do you see my vision
\\When people are passing drinks on the table
\\Do they see what the person beside them sees?
\\I'm asking do you see me?
\\Or am I like God \dots 
\\I apparently exist but you can't find me
\\I'm in my own thoughts and my thoughts are taking over
\\My unconscious is becoming my conscious
\\And the conscious is dying
\\I'm lying down
\\My heart is stranded on the ocean
\\Because when rhymes are going through my mind
\\They're pretty neat
\\But I'm sadly done today
\\Maybe tomorrow will be better if I'm not dead then
\\I ask if I'm okay
\\I can't lie
\\Maybe today may not be my day
\\But this life I live in is mine
\\So even if it's not my day
\\Maybe tomorrow they're waiting in the line
\\To be silenced by my rhymes
\\But I'm not making poems for people
\\I'm making them for me
\\Trilogy taking a piece of my heart and putting it on paper
\\I'm crying because poems are getting personality
\\I have a dream
\\And that is \dots 
\\I want to be the best poet to ever be 
\end{document}